### 2018-02-20 paper.tex
setup files

\documentclass{article}

\begin{document}
First document. This is a simple example, with no 
extra parameters or packages included.
\end{document}

### 2018-02-20 paper.tex
will be trying to float hiast.jpg properly
stuff are working need some formatting

@@
-\documentclass{article}
+\documentclass[12pt, a4paper]{article}
 
+% including packages
+\usepackage[utf8]{inputenc}
+\usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage{wrapfig}
+
+\graphicspath{ {images/} }
+
+% title
+\title{Using Genetic Algorithms to Find Approximations for the Minimum Vertex Cover Problem}
+\author{}
+\date{}
+
+% document begins here
 \begin{document}
-First document. This is a simple example, with no 
-extra parameters or packages included.
+
+{
+\begin{wrapfigure}{r}{0.25\textwidth}
+\hfill
+\includegraphics[width=0.9\linewidth]{hiast}
+\end{wrapfigure}
+
+\setlength{\parindent}{0cm}
+Syrian Arab Republic\\
+Higher Institute for Applied Sciences and Technology\\
+Informatics Department\\
+Fourth Year\\
+}
+
+%\begin{flushleft}
+\noindent Syrian Arab Republic\\
+Higher Institute for Applied Sciences and Technology\\
+Informatics Department \\
+Fourth Year\\
+%\end{flushleft}
+
+{\let\newpage\relax\maketitle}
+
+\begin{center}
+\begin{align*}
+\text{Author: }					& \textit{Farouk Hjabo} \\
+\text{Academic Supervisor: }	& \textit{Dr. Said Desouki} \\
+\text{General Supervisor: }		& \textit{Dr. Kadan Aljoumaa} \\
+\text{Langauge Supervisor: }	& \textit{Mr. Fahmi Alammareen} \\
+\end{align*}
+\end{center}
+
+\vfill
+\centerline{\date{\today}}
+\pagebreak
+
+\section{intro}
+hislhdf
+\subsection{intro-sub}
+dfsfafs
+
+\section{conc}
+lsdjfslfd
 \end{document}

### 2018-02-20 paper.tex
done. will be looking for better formatting

@@
 {
-\begin{wrapfigure}{r}{0.25\textwidth}
+\begin{wrapfigure}{r}{0.20\textwidth}
 \hfill
@@
 
-\setlength{\parindent}{0cm}
+\ \\[1.0mm]
 Syrian Arab Republic\\
@@
 }
-
-%\begin{flushleft}
-\noindent Syrian Arab Republic\\
-Higher Institute for Applied Sciences and Technology\\
-Informatics Department \\
-Fourth Year\\
-%\end{flushleft}
 

### 2018-02-20 paper.tex
perfectly sufficiant. still looking for better

@@
-\documentclass[12pt, a4paper]{article}
+\documentclass[12pt]{article}
 
@@
 \usepackage{wrapfig}
+\usepackage[a4paper, total={6in, 8in}]{geometry}
 
@@
 \section{intro}
-hislhdf
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
+tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
+quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
+consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
+cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
+proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
+tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
+quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
+consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
+cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
+proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
 \subsection{intro-sub}

### 2018-02-20 paper.tex
finished cover page

@@
 \graphicspath{ {images/} }
+\newcommand{\lineSeparationLength}{2mm}
 
@@
 
+% cover page
 {
-\begin{wrapfigure}{r}{0.20\textwidth}
+\begin{wrapfigure}{r}{0.25\textwidth}
 \hfill
@@
 
-\ \\[1.0mm]
-Syrian Arab Republic\\
-Higher Institute for Applied Sciences and Technology\\
-Informatics Department\\
-Fourth Year\\
+\ \\[\lineSeparationLength]
+Syrian Arab Republic \\[\lineSeparationLength]
+Higher Institute for Applied Sciences and Technology \\[\lineSeparationLength]
+Informatics Department \\[\lineSeparationLength]
+Fourth Year
 }
 
+\vspace{25mm}
 {\let\newpage\relax\maketitle}
 
+\vspace{5mm}
 \begin{center}
@@
 
+% first page starts here
 \section{intro}
@@
 lsdjfslfd
+
+% end of document
 \end{document}

### 2018-02-20 paper.tex
finished overall template

@@
 \newcommand{\lineSeparationLength}{2mm}
+%\renewcommand\thesection{\Roman{section}}
 
@@
 % cover page
+\pagenumbering{gobble}
+\addcontentsline{toc}{section}{Cover Page}
+
 {
@@
 
+\vspace{-10mm}
+\begin{center}
+Keywords: genetic algorithms, NP, non-determenstic.
+\end{center}
+
 \vspace{5mm}
@@
 
-% first page starts here
-\section{intro}
+% abstract page
+\pagenumbering{roman}
+\setcounter{page}{2}
+\addcontentsline{toc}{section}{Abstract}
+
+\begin{abstract}
 Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
@@
 proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
-tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
-quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
-consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
-cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
-proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\end{abstract}
 
-\subsection{intro-sub}
-dfsfafs
+\pagebreak
 
-\section{conc}
-lsdjfslfd
+% table of contents page
+\addcontentsline{toc}{section}{Table of Contents}
+\tableofcontents
+\pagebreak
+
+% first page starts here
+\pagenumbering{arabic}
+
+\section{Introduction}
+
+This is the first section.
+
+Lorem  ipsum  dolor  sit  amet,  consectetuer  adipiscing  
+elit.   Etiam  lobortisfacilisis sem.  Nullam nec mi et 
+neque pharetra sollicitudin.  Praesent imperdietmi nec ante. 
+Donec ullamcorper, felis non sodales...
+
+\section{Second Section}
+
+Lorem ipsum dolor sit amet, consectetuer adipiscing elit.  
+Etiam lobortis facilisissem.  Nullam nec mi et neque pharetra 
+sollicitudin.  Praesent imperdiet mi necante...
+
+\subsection{First Subsection}
+Praesent imperdietmi nec ante. Donec ullamcorper, felis non sodales...
+
+\section*{Unnumbered Section}
+Lorem ipsum dolor sit amet, consectetuer adipiscing elit.  
+Etiam lobortis facilisissem
 

### 2018-02-21 paper.tex
added navigation to the table of contents + navigation bar in the pdf
recovered from random error
will be adding references
added references properly
will be trying biblatex

--- 2018-02-20 paper.tex
@@
 \usepackage[a4paper, total={6in, 8in}]{geometry}
+\usepackage{hyperref}
+\usepackage{hypcap}
 
+% preferences
 \graphicspath{ {images/} }
 \newcommand{\lineSeparationLength}{2mm}
+\hypersetup{colorlinks=true, allcolors=black}
 
@@
 % cover page
+\pagenumbering{roman}
+\cleardoublepage\phantomsection\addcontentsline{toc}{section}{Cover Page}
+
 {
@@
 
+\vspace{-10mm}
+\begin{center}
+Keywords: genetic algorithms, NP-complete, combinatorial optimization, non-deterministic algorithms, approximation algorithms, minimum vertex cover.
+\end{center}
+
 \vspace{5mm}
@@
 \centerline{\date{\today}}
+\thispagestyle{empty}
 \pagebreak
 
-% first page starts here
-\section{intro}
+% abstract page
+\cleardoublepage\phantomsection\addcontentsline{toc}{section}{Abstract}
+
+\begin{abstract}
 Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
@@
 proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\end{abstract}
+
+\pagebreak
+
+% table of contents page
+\cleardoublepage\phantomsection\addcontentsline{toc}{section}{Contents}
+\tableofcontents
+\pagebreak
+
+% first page starts here
+\pagenumbering{arabic}
+
+\section{Introduction}
 Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
@@
 
-\subsection{intro-sub}
-dfsfafs
+\section{Genetic Algorithms}
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
+tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
+quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
+consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
+cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
+proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 
-\section{conc}
-lsdjfslfd
+\section{The Minimum Vertex Cover Problem}
+Lorem \cite{einstein} ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
+tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
+quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
+consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
+cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
+proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+\section{Experimental Results}
+Lorem \cite{dirac} ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
+tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
+quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
+consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
+cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
+proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+\section{Conclusion}
+Lorem \cite{ctan} ipsum dolor \cite{knuth-acp} sit amet, consectetur adipisicing elit, sed do eiusmod
+tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
+quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
+consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
+cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
+proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+\pagebreak
+
+\cleardoublepage\phantomsection\addcontentsline{toc}{section}{References}
+\bibliographystyle{abbrv}
+\bibliography{references}
 

### 2018-02-21 paper.tex
finished biblatex setup

@@
 \usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
 \usepackage{amsmath}
@@
 \usepackage{hypcap}
+\usepackage[autostyle]{csquotes}
+\usepackage[giveninits=true]{biblatex}
 
@@
 \hypersetup{colorlinks=true, allcolors=black}
+\addbibresource{references.bib}
 
@@
 \section{Conclusion}
-Lorem \cite{ctan} ipsum dolor \cite{knuth-acp} sit amet, consectetur adipisicing elit, sed do eiusmod
+Lorem \cite{ctan} ipsum dolor \cite{knuth-acp, ctan} sit amet, consectetur adipisicing elit, sed do eiusmod
 tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
@@
 \cleardoublepage\phantomsection\addcontentsline{toc}{section}{References}
-\bibliographystyle{abbrv}
-\bibliography{references}
+%\bibliographystyle{abbrv}
+%\bibliography{references}
+\printbibliography
 

### 2018-02-21 paper.tex
added basic references to references.bib will start writing the content

@@
 \usepackage[autostyle]{csquotes}
-\usepackage[giveninits=true]{biblatex}
+\usepackage[]{biblatex}
 
@@
 \addbibresource{references.bib}
+\ExecuteBibliographyOptions{
+	giveninits=true,
+	isbn=false,
+	doi=false,
+	url=false
+}
 
@@
 \section{Conclusion}
-Lorem \cite{ctan} ipsum dolor \cite{knuth-acp, ctan} sit amet, consectetur adipisicing elit, sed do eiusmod
+Lorem \cite{ctan} ipsum dolor \cite{knuth-acp, ctan,
+khuri1994evolutionary, back1994evolutionary}
+\cite{goldberg1989genetic, coley1999introduction} sit amet, consectetur adipisicing elit, sed do eiusmod
 tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,

### 2018-02-21 paper.tex
before session

@@
 }
+\setlength{\parskip}{1em}
 
@@
 \section{Introduction}
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
-tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
-quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
-consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
-cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
-proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Once the NP-hardness of a combinatorial optimization
+problem is established, the search for an optimal solution
+is abandoned. The goal then becomes one of finding a
+good heuristic, i.e. a polynomial running time algorithm
+that can find solutions close to the optimal. In most cases,
+traditional heuristics are problem dependent; a heuristic is
+tailored to the specific problem it is trying to solve.
+
+In this paper, we present an alternative approach that
+uses genetic algorithms as a generalized heuristic for solving NP-hard combinatorial optimization problems. The
+application of a genetic algorithm is demonstrated here for
+the \emph{minimum vertex cover} problem. These algorithms
+have been successfully applied to a broad range of problems. This wide range can be tackled by genetic algorithms
+mainly due to the fact that they work with an encoding of
+the domain rather than with the problem domain itself.
 
@@
 \section{Conclusion}
-Lorem \cite{ctan} ipsum dolor \cite{knuth-acp, ctan,
-khuri1994evolutionary, back1994evolutionary}
-\cite{goldberg1989genetic, coley1999introduction} sit amet, consectetur adipisicing elit, sed do eiusmod
+Lorem \cite{ctan} ipsum dolor \cite{khuri1994evolutionary}
+sit amet, consectetur adipisicing elit, sed do eiusmod
 tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,

### 2018-02-22 paper.tex
will add steps under enumerate enviroment

@@
 \usepackage[]{biblatex}
+\usepackage{amsfonts}
 
@@
 \setlength{\parskip}{1em}
+\newcommand{\textem}[1]{\textbf{\textit{#1}}}
 
@@
 
+\vfill
+
+\noindent
+\textit{
+``It is not the strongest of the species that survives,
+nor the most intelligent, but the one most responsive
+to change.''
+}
+\begin{flushright}
+\setlength{\parskip}{0em}
+\rm --- Charles Darwin
+\end{flushright}
+
 \pagebreak
@@
 \section{Genetic Algorithms}
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
-tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
-quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
-consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
-cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
-proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\subsection{The Intuition Behind GAs}
+Genetic Algorithms (GAs)~\cite{goldberg1989genetic} are population based
+search algorithms, where by repeated use of genetic operations,
+such as \textem{mutation}, \textem{selection}, \textem{crossover}, etc...
+Successive new generations of better populations in the direction of
+search objectives are created. They are inspired by Darwinian principles
+based on natural evolution. In other words, the main idea behind genetic
+algorithms is that only the \textem{fittest} individuals will survive.\\
+Main advantage of genetic algorithms is that they ideally do not make
+any assumption about the underlying problem, hence they are suitable to tackle
+a wide range of diverse problems in
+engineering, art, biology, economics, marketing, genetics,
+operations research, robotics, social sciences, physics, politics, chemistry,
+etc...
+
+\noindent
+So what is a GA? A typical GA consists of the following:
+\vspace{-5mm}
+\begin{enumerate}
+\setlength{\parskip}{0em}
+\item a number, or \textem{population}, of candidate solutions to the problem.
+\item a way of calculating how good or bad the individual solutions within the
+population are. i.e. how \textem{fit} an individual is?
+\item a method for mixing fragments of the better solutions to form new, on
+average even better solutions. Which permits the population to \textem{evolve} naturally.
+\item a \textem{mutation} operator to avoid permanent loss of diversity within the
+solutions. This allows introducing new information in the population.
+\end{enumerate}
+
+\subsection{Typical GA Schema}
+The basic iteration cycle of a genetic algorithm proceeds on a population
+of individuals, each of which represents a search point in the space
+of potential solutions of a given optimization problem.
+In case of a canonical genetic algorithm, each individual is a binary vector
+$ \vec{x} = ( x_1, x_2, \dots, x_n ) \in \{0, 1\}^n $
+of fixed length $n$. The fitness function
+$ f: \{0, 1\}^n \rightarrow \mathbb{R} $
+provides a quality measure which is used by the selection procedure to direct
+the search towards regions of the search space where the
+average fitness of the population increases. The recombination operator
+allows for the exchange of information between different individuals, and
+mutation introduces innovation into the population.
+
+After a uniform random initialization of the population
+the evolution proceeds by iterating the steps selection,
+recombination (crossover), and mutation (see figure~\ref{fig:ga})
+until a termination criterion is fulfilled.
+In most cases, the algorithm is terminated after a certain number of
+iterations of the basic cycle or when a satisfactory fitness
+level has been reached.
+
+The recombination (crossover) operator allows for the
+exchange of information between different individuals. The
+original one-point crossover [9] works on two parent individuals
+(which are randomly chosen from the population, see the next paragraph)
+by choosing a crossover point $ \chi \in \{1, \dots, n-1 \} $
+at random and exchanging all bits after the $ \chi^{\text{th}} $ one
+between both individuals. The crossover rate
+$ p_c \ (\text{e.g. } p_c \approx 0.6) $
+determines the probability to undergo crossover (see todo for more details).
+The crossover operator can be extended to a generalized
+multi-point crossover [10] or even to uniform crossover,
+where an it is randomly decided for each bit
+whether to exchange it or not [19]. The strong mixing effect
+introduced by uniform crossover is sometimes helpful
+to overcome local optima.
+
+Normally, selection in genetic algorithms is a probabilistic operator
+which uses the relative fitness 
+$ p_s \left( \vec{x_i} \right) = 
+f \left( \vec{x_i} \right) / \sum_{j=1}^uf \left( \vec{x_j} \right) $
+to serve as selection probabilities
+($u$ denotes the population size). This selection operator
+is called proportional selection. If the problem under
+consideration is a minimization one, or if the fitness
+function can take negative values, then $ f \left( \vec{x_i} \right) $ has to be
+linearly transformed before calculating selection probabilities.
+This technique known as linear dynamic scaling is commonly used
+in genetic algorithms (see [13], pp. 123-124, or [14]).
+
+Innovation, i.e. new information, is introduced into the
+population by means of mutation, which works by inverting
+bits with a small probability
+$ p_m \ (\text{e.g. } p_m \approx 0.001) $
+Though mutation is often interpreted as a rather unimportant operator
+in genetic algorithms [9], recent theoretical
+work gives strong evidence for an appropriate choice of a
+mutation rate $ p_m = 1/n $ on many problems [2; 12].
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=1\textwidth]{ga}
+\caption{general schema for genetic algorithms}
+\label{fig:ga}
+\end{figure}
 
@@
 \section{Conclusion}
-Lorem \cite{ctan} ipsum dolor \cite{khuri1994evolutionary}
 sit amet, consectetur adipisicing elit, sed do eiusmod
-tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
-quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
-consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
-cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
-proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 

### 2018-02-22 paper.tex
didn't do that, instead refactored text now i will be doing that

@@
 In case of a canonical genetic algorithm, each individual is a binary vector
-$ \vec{x} = ( x_1, x_2, \dots, x_n ) \in \{0, 1\}^n $
+$ \vec{x} = ( x_1, \dots, x_n ) \in \{0, 1\}^n $
 of fixed length $n$. The fitness function
@@
 allows for the exchange of information between different individuals, and
-mutation introduces innovation into the population.
-
-After a uniform random initialization of the population
-the evolution proceeds by iterating the steps selection,
-recombination (crossover), and mutation (see figure~\ref{fig:ga})
-until a termination criterion is fulfilled.
+mutation introduces innovation into the population. \\
+This cycle is repeated until a termination criterion is fulfilled.
 In most cases, the algorithm is terminated after a certain number of
@@
 level has been reached.
+refer to figure~\ref{fig:ga} for a visual representation of this process.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=1\textwidth]{ga}
+\caption{general schema for genetic algorithms}
+\label{fig:ga}
+\end{figure}
+
+The population size (denoted as $u$) depends on the nature of the problem,
+but typically contains several hundreds or thousands of possible solutions.
+Often, the initial population is generated randomly, allowing the entire range
+of possible solutions (the search space).
+Occasionally, the solutions may be `seeded' in areas where optimal solutions
+are likely to be found.
+
+Normally, selection in genetic algorithms is a probabilistic operator
+which uses the relative fitness 
+$ p_s \left( \vec{x_i} \right) = 
+f \left( \vec{x_i} \right) / \sum_{j=1}^uf \left( \vec{x_j} \right) $
+to serve as selection probabilities
+($u$ denotes the population size). This selection operator
+is called proportional selection. If the problem under
+consideration is a minimization one, or if the fitness
+function can take negative values, then $ f \left( \vec{x_i} \right) $ has to be
+linearly transformed before calculating selection probabilities.
+This technique known as linear dynamic scaling is commonly used
+in genetic algorithms (see [13], pp. 123-124, or [14]).
 
@@
 
-Normally, selection in genetic algorithms is a probabilistic operator
-which uses the relative fitness 
-$ p_s \left( \vec{x_i} \right) = 
-f \left( \vec{x_i} \right) / \sum_{j=1}^uf \left( \vec{x_j} \right) $
-to serve as selection probabilities
-($u$ denotes the population size). This selection operator
-is called proportional selection. If the problem under
-consideration is a minimization one, or if the fitness
-function can take negative values, then $ f \left( \vec{x_i} \right) $ has to be
-linearly transformed before calculating selection probabilities.
-This technique known as linear dynamic scaling is commonly used
-in genetic algorithms (see [13], pp. 123-124, or [14]).
-
 Innovation, i.e. new information, is introduced into the
@@
 mutation rate $ p_m = 1/n $ on many problems [2; 12].
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=1\textwidth]{ga}
-\caption{general schema for genetic algorithms}
-\label{fig:ga}
-\end{figure}
 

### 2018-02-23 paper.tex
commiting before sleep

@@
 \usepackage{amsfonts}
+\usepackage{algorithm}
+\usepackage[end]{algpseudocode}
 
@@
 \newcommand{\textem}[1]{\textbf{\textit{#1}}}
+\newtheorem{lemma}{Lemma}
 
@@
 application of a genetic algorithm is demonstrated here for
-the \emph{minimum vertex cover} problem. These algorithms
+the \textit{minimum vertex cover} problem. These algorithms
 have been successfully applied to a broad range of problems. This wide range can be tackled by genetic algorithms
@@
 
+\paragraph{Initialization}
 The population size (denoted as $u$) depends on the nature of the problem,
@@
 
+\paragraph{Selection}
 Normally, selection in genetic algorithms is a probabilistic operator
@@
 
+\paragraph{Crossover}
 The recombination (crossover) operator allows for the
@@
 original one-point crossover [9] works on two parent individuals
-(which are randomly chosen from the population, see the next paragraph)
+(which are randomly chosen from the population, see the previous paragraph todo)
 by choosing a crossover point $ \chi \in \{1, \dots, n-1 \} $
@@
 
+\paragraph{Mutation}
 Innovation, i.e. new information, is introduced into the
@@
 
+For better understanding of figure~\ref{fig:ga}
+\begin{algorithm}
+\caption{Gentic Algorithm$\left( n, u, p_c, p_m, f \right)$}
+\label{alg:ga}
+
+\begin{algorithmic}[1]
+
+\State $ P \gets \{ \} $
+\Comment{$P$ contains the population}
+\Loop \ $u$ times
+\Comment{initialization}
+\State add a randomly generated binary vector of length $n$ to $P$
+\EndLoop
+
+\While{termination criterion is not fulfilled}
+\State $Q \gets \{ \}$
+\Comment{$Q$ will hold the new generation}
+\Loop \ $u/2$ times
+
+\State select $x, y$ from $P$ using proportional selection
+\Comment{selection}
+\State with probability $p_c$ perform crossover between $x, y$
+\Comment{crossover}
+\State for each bit in $x$ flip it with probability $p_m$
+\Comment{mutation}
+\State for each bit in $y$ flip it with probability $p_m$
+\Comment{mutation}
+\State add $x, y$ to $Q$
+
+\EndLoop
+
+\State $P \gets Q$
+\EndWhile
+
+\end{algorithmic}
+
+\end{algorithm}
+
 \section{The Minimum Vertex Cover Problem}
-Lorem \cite{einstein} ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
-tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
-quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
-consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
-cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
-proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+The problem of finding a minimum vertex cover is a classical
+optimization problem in computer science and is a typical
+example of an NP-hard optimization problem that has an
+approximation algorithm.
+The mvcp of an undirected graph $G = (V, E)$ where $V$ is
+the set of vertices and $E$ denotes the set of edges, consists
+in finding the smallest subset $V' \subseteq V$ such that
+$\forall \langle i, j \rangle \in E$, we have $i \in V'$ or $j \in V'$ (or both).
+$V'$ is said to be a vertex cover of $G$. The following is a formal definition of
+the mvcp in which we make use of Stinson's terminology
+for combinatorial optimization problems [14]:
+
+{
+\setlength{\parskip}{0em}
+\paragraph{Problem instance:}
+A graph $G = (V, E)$, where $V = \{1, 2, \dots, n\}$
+is the set of vertices and $E \subseteq V \times V$ the
+set of edges. An edge between vertices $i, j$ is denoted
+by the pair $\langle i, j \rangle \in E$. We define the adjacency
+matrix $e_{ij}$ according to:
+\[
+e_{ij} =
+\begin{cases}
+1 & \text{if } \langle i, j \rangle \in E \\
+0 & \text{otherwise}
+\end{cases}
+\]
+especially, we have $e_{ii} = 0$
+
+\paragraph{Feasible solution:} A set $V' \subseteq V$ such that
+$\forall \langle i, j \rangle \in E, i \in V' \vee j \in V'$
+\paragraph{Objective function:} The size $|V'|$ of the vertex cover $V'$.
+\paragraph{Optimal solution:} a vertex cover $V'$ that minimizes $|V'|$.
+}
+
+an interesting property of the mvcp is that by
+solving it, we also have a solution for two other
+graph problems: the \textit{maximum independent set problem}%
+\footnote{%
+misp: given $G = (V, E)$, find the largest subset $V' \subseteq V$
+such that $\forall i, j \in V', \langle i, j \rangle \notin E$
+}
+and the \textit{maximum clique problem}%
+\footnote{%
+mcp: given $G = (V, E)$, find the largest subset $V' \subseteq V$
+such that $\forall i, j \in V', \langle i, j \rangle \in E$
+}
+The close relationship between these problems
+is characterized by the following lemma [6].
+
+\begin{lemma}
+\ \\[3mm]
+For any graph $G = (V, E)$ and $V' \subseteq V$, the following
+statements are equivalent:
+\begin{itemize}
+\vspace{-3mm}
+\setlength{\parskip}{0.5em}
+\item $V'$ is the minimum vertex cover of $G$.
+\item $V - V'$ is the maximum independent set in $G$.
+\item $V - V'$ is the maximum clique in $\bar{G} = (V, \bar{E})$, where \\
+$\bar{E}=\left\{ \langle i, j \rangle\in V \times V :
+\langle i, j \rangle \notin E \right\}$
+\end{itemize}
+\end{lemma}
+Consequently, one can obtain a solution of the maximum independent set
+problem by taking the complement of the solution to the minimum vertex cover
+problem. A solution to the maximum clique problem is obtained by
+taking the complement of the minimum vertex cover of $\bar{G}$.
+
+\subsection{Related Algorithms}
+Since we are interested in covering all the edges of the
+given graph by using as few nodes as possible, one might
+be tempted to use a greedy-based heuristic to tackle the
+mvcp. The algorithm consists in repeatedly selecting a
+vertex of highest degree (the node that covers as many
+of the remaining edges as possible), and removing all
+of its incident edges. This is not a good strategy as
+was demonstrated by Papadimitriou and Steiglitz ([10],
+p. 407). \\
+They considered regular graphs, each of which
+consists of three levels. The first two levels have the same
+number of nodes while the third level has two nodes less
+than the number of nodes found on the previous two
+levels. More precisely, each graph consists of $n = 3k + 4 (k \geq 1)$
+nodes; $k+2$ nodes on the first level, labeled $1, 2, \dots, k+2$;
+followed by $k+2$ nodes on the second level, labeled $k+3, \dots, 2k+4$;
+while the $k$ nodes of the third level are labeled $2k+5, \dots, 3k+4$.
+The regular graph for $k = 4$ can be found in figure~\ref{fig:g1}.
+A minimum vertex cover is obtained by choosing all
+the nodes of the second level, but the greedy strategy
+would start with the nodes of the third level, since these
+have highest degree. Consequently, the greedy strategy
+finds a solution of size $2k + 2$ (since it has to select $k + 2$
+nodes in addition to the nodes of the third level), while
+the optimal solution has size $k + 2$.
+However this algorithm is not totally useless. It may be shown that it always
+achieves the ratio $\Theta(\lg n)$, where $n$ is the number of vertices.
+That is, if $C^*(n)$ is the size of the optimal
+solution and $C(n)$ is the size of the solution found by the aforementioned
+algorithm. Then we have $\frac{C(n)}{C^*(n)} = \Theta(\lg n)$ [9], p-323.
+
+Fortunately, a simpler and better algorithm exists.
+The following simple algorithm is surprisingly the
+best approximation algorithm known for the mvcp ([9],
+p. 301).
+
+\begin{algorithm}
+\caption{vercov}
+\label{alg:vercov}
+\begin{algorithmic}[1]
+
+\State $C \gets \{ \}$
+\Comment{$C$ contains the vertex cover being constructed}
+\State $E' \gets E$
+\While{$E' \neq \phi$}
+\State randomly choose $ \langle u, v \rangle \in E'$
+\State $C \gets C \cup \{u, v\}$
+\State $E' \gets E' -
+\{ \langle x, y \rangle \in E' : x=u \vee y=v \vee x=v \vee y=u \}$
+\State \Comment{remove from $E'$ every edge incident on either $u$ or $v$}
+\EndWhile
+\State \Return $C$
+
+\end{algorithmic}
+\end{algorithm}
+
+This is a \textit{2-approximation algorithm}. Which means that
+the size of the vertex cover
+it returns is guaranteed to be no more than twice the
+size of an optimal vertex cover ([1], p. 968).
+More precisely, if $C^*$ is the size of the optimal
+solution and $C$ is the size of the solution returned by Algorithm~\ref{alg:vercov}
+then the inequality $C \leq 2C^*$ must hold (notice that here the approximation
+doesn't depend on the number of vertices $n$).
+
+\subsection{GA for the mvcp}
+In order to apply GA to solve the mvcp, a cover $V'$ is represented
+by a binary vector $\vec{x} = x_1x_2 \dots x_n$ where $x_i = 1$ if
+the $i^{\text{th}}$ node is in $V'$, and $x_i = 0$ if it is not.
+Using this representation, genetic algorithm is applied to minimize the following
+fitness function: [0] \\
+\begin{equation}
+\label{eq:f}
+\begin{split}
+f(\vec{x})	&= \sum_{i=1}^{n} \left( x_i+n \cdot (1-x_i) \cdot
+			   \sum_{j=i}^{n} (1-x_j) e_{ij} \right) \\
+ 			&= \sum_{i=1}^{n} x_i + n \cdot \sum_{i=1}^{n}
+			   \sum_{j=i}^{n} (1-x_i) \cdot (1-x_j) \cdot e_{ij}
+\end{split}
+\end{equation}
+The term $ \sum_{i=1}^{n} x_i $ of $ f(\vec{x}) $ determines the size of the
+potential vertex cover represented by $\vec{x}$, while the term
+$ n \cdot \sum_{i=1}^{n} \sum_{j=i}^{n} (1-x_i) \cdot (1-x_j) \cdot e_{ij} $
+penalizes sets $V'$ that
+are not covers by adding a penalty of magnitude $n$ for
+each edge $e_{ij}$ for which $i \notin V' \wedge j \notin V'$
+(note that $e_{ii}$ is previously defined to be zero).
+Consequently, any infeasible solution will have a fitness greater than
+or equal to $n$, and for any feasible solution the second term will
+drop to zero.
+This fitness function was developed according to the
+following design principles that are important for a
+successful penalty function approach [11 $||$ 13 $||$ 7]:
+
+\begin{itemize}
+\vspace{-3mm}
+
+\item Infeasible binary vectors are guaranteed to yield fitness
+values which are inferior to fitness values of
+the worst feasible solutions.
+
+\item The penalty should be graded, i.e., fitness values
+should improve as solutions approach feasible regions
+of the search space. In other words, the more edges a solution
+covers, the fitter it is. notice that this is guaranteed by the
+second term in equation~\ref{eq:f}, where for each uncovered edge
+the fitness is penalized with the value of $n$.
+\end{itemize}
+
+The experiments reported in section~\ref{sec:er} are performed
+by using a genetic algorithm with a population size of
+$u = 50$, a mutation rate $p_m = 1/n$, crossover rate
+$p_c = 0.6$, proportional selection, and two-point crossover.
+As reported in [2, 12], the latter is expected to perform
+better than the traditional one-point crossover.
 
 \section{Experimental Results}
-Lorem \cite{dirac} ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
-tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
-quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
-consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
-cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
-proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\label{sec:er}
+For the experimental tests, random graphs of size $n = 100$ with different
+edge densities $d$, $d \in \{0.1, 0.2, 0.3, 0.4, 0.5\}$, are used.
+an edge density of d = 0:1 means that an edge is placed between two
+nodes with a probability of 0.1.
 

### 2018-02-23 paper.tex
stupid code folding erroe

@@
 \newtheorem{lemma}{Lemma}
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+\algnewcommand\algorithmicto{\textbf{to}}
+\algrenewtext{For}[3]%
+{\algorithmicfor\ #1 = #2 \algorithmicto\ #3 \algorithmicdo}
 
@@
 
-\begin{figure}[ht]
+\begin{figure}[!htbp]
 \centering
@@
 \subsection{Related Algorithms}
+\label{sec:ra}
 Since we are interested in covering all the edges of the
@@
 while the $k$ nodes of the third level are labeled $2k+5, \dots, 3k+4$.
-The regular graph for $k = 4$ can be found in figure~\ref{fig:g1}.
+The regular graph for $k = 3$ can be found in figure~\ref{fig:ps}.
 A minimum vertex cover is obtained by choosing all
@@
 However this algorithm is not totally useless. It may be shown that it always
-achieves the ratio $\Theta(\lg n)$, where $n$ is the number of vertices.
+achieves the ratio $\Theta(\lg n)$\footnote{$f(n) = \Theta(g(n)) \iff
+\exists \alpha, \beta, n_0 : \forall n \geq n_0, \ 
+\alpha \cdot g(n) \leq f(n) \leq \beta \cdot g(n)
+$},
+where $n$ is the number of vertices.
 That is, if $C^*(n)$ is the size of the optimal
@@
 algorithm. Then we have $\frac{C(n)}{C^*(n)} = \Theta(\lg n)$ [9], p-323.
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[width=1\textwidth]{ps}
+\caption{Construction of the regular graph after Papadimitriou
+and Steiglitz with $k=3$.}
+\label{fig:ps}
+\end{figure}
 
@@
 \begin{algorithm}
-\caption{vercov}
+\caption{vercov($G = (V, E)$)}
 \label{alg:vercov}
@@
 \State randomly choose $ \langle u, v \rangle \in E'$
+\label{alg:rand}
 \State $C \gets C \cup \{u, v\}$
@@
 More precisely, if $C^*$ is the size of the optimal
-solution and $C$ is the size of the solution returned by Algorithm~\ref{alg:vercov}
+solution and $C$ is the size of the solution returned by algorithm~\ref{alg:vercov}
 then the inequality $C \leq 2C^*$ must hold (notice that here the approximation
@@
 \subsection{GA for the mvcp}
+\label{sec:GAmvcp}
 In order to apply GA to solve the mvcp, a cover $V'$ is represented
@@
 better than the traditional one-point crossover.
+The termination criterion is specified in section~\ref{sec:er}.
 
@@
 \label{sec:er}
-For the experimental tests, random graphs of size $n = 100$ with different
+For the experimental tests,
+the genetic algorithm software package GENEsYs is used [1]misp.
+This implementation is based on the widely used GENESIS software by Grefenstette
+(see [3], pp. 374-377 misp), but allows for more 
+flexibility concerning genetic operators and data monitoring.
+The parameter settings for our experiments are
+given in section~\ref{sec:GAmvcp}.
+
+Multiple problem instances are used to demonstrate the applicability of GAs to tackle the mvcp
+The results in table~\ref{fig:t1}
+and table~\ref{fig:t2} correspond to the first test set, which consists of
+five random graphs of size $n = 100$ with different
 edge densities $d$, $d \in \{0.1, 0.2, 0.3, 0.4, 0.5\}$, are used.
-an edge density of d = 0:1 means that an edge is placed between two
+An edge density of $d = 0.1$ means that an edge is placed between two
 nodes with a probability of 0.1.
+Moreover we construct the graphs in a way that guarantees an optimum of quality 55
+(we set $k = 55$ in algorithm~\ref{alg:gen}).
+In addition to the regular graphs introduced by
+Papadimitriou and Steiglitz and described in section~\ref{sec:ra}.
+Recall that these graphs contain $n=3k+4 (k \geq 1)$ nodes distributed on three levels.
+They can be scaled up by choosing high values for $k$.
+A graph instance of the regular graph of size $n = 100 (k=32)$ is chosen.
+
+\begin{algorithmic}[1]
+
+\State randomly select $V' = \{i_1, \dots, i_k\} \subseteq V = \{1, \dots, n\}$
+\Comment{randomly select k different nodes}
+\For
+
+\State $C \gets \{ \}$
+\Comment{$C$ contains the vertex cover being constructed}
+\State $E' \gets E$
+\While{$E' \neq \phi$}
+\State randomly choose $ \langle u, v \rangle \in E'$
+\label{alg:rand}
+\State $C \gets C \cup \{u, v\}$
+\State $E' \gets E' -
+\{ \langle x, y \rangle \in E' : x=u \vee y=v \vee x=v \vee y=u \}$
+\State \Comment{remove from $E'$ every edge incident on either $u$ or $v$}
+\EndWhile
+\State \Return $C$
+
+\end{algorithmic}
+\end{algorit
+For each of these graphs, a total of
+$N = 100$ independent runs of the genetic algorithm is performed.
+The results are summarized in table~\ref{fig:t1} for the best
+fitness values that were encountered during the 100 runs.
+For each problem instance, the different fitness values that were
+obtained and their frequencies are recorded.
+Furthermore, the average fitness value $\bar{f}$ over
+all 100 runs is indicated at the bottom of the table.
+For example, the first column in table~\ref{fig:t1} indicates
+that the best obtained fitness value in 1 of the 100 runs was $f(\vec{x}) = 53$,
+the best obtained fitness value in 1 of the 100 runs was $f(\vec{x}) = 54$,
+the best obtained fitness value in 3 of the 100 runs was $f(\vec{x}) = 55$, and so on...
+And the average of these values is indicated by $\bar{f}$, which is the average value of
+the best obtained fitness values over the 100 runs.
+
+As a termination criterion for the genetic algorithm, a bound for the total number of function evaluations is set.
+For example The total number of function evaluations per single run is chosen to be $2 \cdot 10^4$ in table~\ref{fig:t1}.
+That is, the algorithm terminates when $2 \cdot 10^4$ evaluations of the fitness function
+had occurred.
+This bound is indicated as an index $t$ in the notation $f_t(\vec{x})$.
+Consequently, only a small fraction of the search space is explored by the genetic algorithm.
+This fraction is about $ 2 \cdot 10^4 / 2^{100} \approx 1.6 \cdot 10^{-24} \% $ for the first test set.
+and it is about $ 4 \cdot 10^4 / 2^{200} \approx 2.5 \cdot 10^{-54} \% $ for the second test set.
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[width=1\textwidth]{t1}
+\caption{general schema for genetic algorithms}
+\label{fig:t1}
+\end{figure}
+
+For each of the problems in the first test set, a total of $N=100$
+independent runs of the vercov algorithm is performed. The results are summarized in table~\ref{fig:t2}.
+Notice that for one problem instance, the results may differ in each run due to the
+non-determinism of the algorithm (see algorithm~\ref{alg:vercov} line~\ref{alg:rand}).
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[width=1\textwidth]{t2}
+\caption{general schema for genetic algorithms}
+\label{fig:t2}
+\end{figure}
+
+To test the behaviour of the genetic algorithm
+as well as the vercov algorithm for an even
+larger problem size, The same experiments were performed for larger graphs
+The results in table~\ref{fig:t3}
+and table~\ref{fig:t4} correspond to the second test set, which consists of
+five random graphs of size $n = 200$ with different
+edge densities $d$, $d \in \{0.1, 0.2, 0.3, 0.4, 0.5\}$, are used.
+Moreover we construct the graphs in a way that guarantees an optimum of quality 110
+(see algorithm~\ref{alg:gen}).
+In addition to a graph instance of the regular graphs introduced by
+Papadimitriou and Steiglitzof of size $n = 220 (k=66)$.
+In this case, the genetic algorithm
+was allowed to run for $4 \cdot 10^4$ function evaluations.
+The corresponding results obtained by the
+genetic algorithm are shown in table~\ref{fig:t3}, while the results
+from the vercov algorithm are presented in table~\ref{fig:t4}.
+See the previous paragraphs for a better understanding of these results.
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[width=1\textwidth]{t3}
+\caption{general schema for genetic algorithms}
+\label{fig:t3}
+\end{figure}
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[width=1\textwidth]{t4}
+\caption{general schema for genetic algorithms}
+\label{fig:t4}
+\end{figure}
+
+\subsection{expermental observations}
 

### 2018-02-23 paper.tex
we're good
going to sleep

@@
 \usepackage[end]{algpseudocode}
+\usepackage{caption}
 
@@
 \label{sec:er}
+\setcounter{figure}{0}
+\captionsetup[figure]{name={Table}}
 For the experimental tests,
@@
 
+\begin{algorithm}
+\caption{Generate$(n, d, k)$}
+\label{alg:gen}
 \begin{algorithmic}[1]
+\algnotext{EndFor}
+\algnotext{EndIf}
 
 \State randomly select $V' = \{i_1, \dots, i_k\} \subseteq V = \{1, \dots, n\}$
-\Comment{randomly select k different nodes}
-\For
-
-\State $C \gets \{ \}$
-\Comment{$C$ contains the vertex cover being constructed}
-\State $E' \gets E$
-\While{$E' \neq \phi$}
-\State randomly choose $ \langle u, v \rangle \in E'$
-\label{alg:rand}
-\State $C \gets C \cup \{u, v\}$
-\State $E' \gets E' -
-\{ \langle x, y \rangle \in E' : x=u \vee y=v \vee x=v \vee y=u \}$
-\State \Comment{remove from $E'$ every edge incident on either $u$ or $v$}
-\EndWhile
-\State \Return $C$
+\State
+\Comment{randomly select k different nodes, these nodes will hold a potential mvc}
+\For{$i$}{$1$}{$n-1$}
+\For{$j$}{$i+1$}{$n$}
+\If{$(\text{Random(0, 1)} \leq d) \wedge (i \in V' \vee j \in V')$}
+\State $e_{ij} = 1$
+\Else
+\State $e_{ij} = 0$
+\EndIf
+\EndFor
+\EndFor
 
 \end{algorithmic}
-\end{algorit
+\end{algorithm}
+
 For each of these graphs, a total of
@@
 
-\subsection{expermental observations}
+\subsection{results comments}
+From these tables, a number of interesting conclusions
+can be drawn. For the random graphs used to compare the
+genetic algorithm and the vercov algorithm,
+it is known by construction that an optimum of quality 55 exists in the first test set,
+(respectively, an optimum of quality 110 exists for the second test set). This optimum is likely to be the
+global optimum, And it is found by the genetic
+algorithm at least once within the $N = 100$ runs that were performed.
+
+Moreover, the randomly constructed problems quickly
+become simpler for the genetic algorithm when the edge
+density is increased. For an edge density of $d \in \{0.4, 0.5\}$, the
+genetic algorithm almost surely finds the global optimum
+of the problems, while vercov algorithm gives a relatively terrible results.
+
+In case of the regular graph after Papadimitriou and
+Steiglitz, the genetic algorithm is able to find the global
+optimum in about $2/3$ of all runs, while the remaining
+runs identify a solution of quality $2k + 2$.
+Whereas, vercov algorithm gives a solution of quality $2k + 2$ in all of the 100 runs as expected.
+Recall that the graphs are constructed
+so as to force the vercov algorithm into yielding solutions
+of quality $2k + 2$.
+The random choice of edges in line~\ref{alg:rand} of the algorithm implies that nodes from either layers one and two, or layers two and three are involved in the solution being constructed, which in turn implies that two layers have to be part of the solution found by the algorithm [10]mvcp.
+
+For the randomly constructed graphs, the vercov algorithm performs
+poorly.
+It barely finds solutions of quality 80 (for graphs of size 100) and 172 (for graphs of size 200).
+The average performance of the vercov algorithm (surprisingly)
+decreases as the edge density is increased.
+i.e. the problems become even harder for the vercov algorithm
+while they become much simpler for the genetic algorithm when
+the edge density increases.
+The average fitness found by the genetic algorithm is notably
+better than the one found by the vercov algorithm.
+One can demonstrate this by calculating
+the ratio of the absolute (or equivalently the relative) error.
+For example, for the first problem instance,
+let $\bar{f}_1, \bar{f}_2$ be the average found by
+the genetic algorithm, vercov algorithm respectively.
+We have $ (\bar{f}_2 - 55) / (\bar{f}_1 - 55) = (86.46 - 55)/(62.61 - 55) \approx 4 = 400\%$
+that is, the error was reduced by a factor of 4.
 
 \section{Conclusion}
-sit amet, consectetur adipisicing elit, sed do eiusmod
+In this work, we have demonstrated that genetic algorithms can be used in a straightforward way t
+good approximate solutions of the minimum vertex cover
+problem. Moreover, the results found by the genetic algorithm are better than those obtained from the best
+known traditional heuristic, the vercov algorithm. These, in addition to other good results obtained on, highly constrained combinatorial optimization
+problems such as the subset sum [7], minimum tardy
+task [7], and multiple knapsack problems [8], give strong
+evidence that genetic algorithms can yield good solutions for a wide range of hard combinatorial optimization problems for which solutions can be represented by
+binary strings.
 

### 2018-02-24 paper.tex
will change figures to table
will do authors the right way

@@
 \usepackage{hyperref}
-\usepackage{hypcap}
+\usepackage[all]{hypcap}
 \usepackage[autostyle]{csquotes}
@@
 \algrenewtext{For}[3]%
-{\algorithmicfor\ #1 = #2 \algorithmicto\ #3 \algorithmicdo}
 
@@
 \tableofcontents
+\pagebreak
+
+% List of Figures and Tables
+\cleardoublepage\phantomsection\addcontentsline{toc}{section}{List of Figures}
+\listoffigures
+
+\phantomsection\addcontentsline{toc}{section}{List of Tables}
+\listoftables
+
+\phantomsection\addcontentsline{toc}{section}{List of Tables}
+\section*{abbrevs}  % Set the left side page header to "Abbreviations"
+\begin{center}
+\begin{tabular}{ l c } 
+ GA & Genetic Algorithm \\ 
+ cell4 & cell5 \\ 
+ cell7 & cell8
+\end{tabular}
+\end{center}
+
 \pagebreak
@@
 \label{sec:er}
-\setcounter{figure}{0}
-\captionsetup[figure]{name={Table}}
 For the experimental tests,
@@
 Multiple problem instances are used to demonstrate the applicability of GAs to tackle the mvcp
-The results in table~\ref{fig:t1}
-and table~\ref{fig:t2} correspond to the first test set, which consists of
+The results in table~\ref{tbl:t1}
+and table~\ref{tbl:t2} correspond to the first test set, which consists of
 five random graphs of size $n = 100$ with different
@@
 $N = 100$ independent runs of the genetic algorithm is performed.
-The results are summarized in table~\ref{fig:t1} for the best
+The results are summarized in table~\ref{tbl:t1} for the best
 fitness values that were encountered during the 100 runs.
@@
 all 100 runs is indicated at the bottom of the table.
-For example, the first column in table~\ref{fig:t1} indicates
+For example, the first column in table~\ref{tbl:t1} indicates
 that the best obtained fitness value in 1 of the 100 runs was $f(\vec{x}) = 53$,
@@
 As a termination criterion for the genetic algorithm, a bound for the total number of function evaluations is set.
-For example The total number of function evaluations per single run is chosen to be $2 \cdot 10^4$ in table~\ref{fig:t1}.
+For example The total number of function evaluations per single run is chosen to be $2 \cdot 10^4$ in table~\ref{tbl:t1}.
 That is, the algorithm terminates when $2 \cdot 10^4$ evaluations of the fitness function
@@
 
-\begin{figure}[!htbp]
+\begin{table}[!htbp]
 \centering
@@
 \caption{general schema for genetic algorithms}
-\label{fig:t1}
-\end{figure}
+\label{tbl:t1}
+\end{table}
 
 For each of the problems in the first test set, a total of $N=100$
-independent runs of the vercov algorithm is performed. The results are summarized in table~\ref{fig:t2}.
+independent runs of the vercov algorithm is performed. The results are summarized in table~\ref{tbl:t2}.
 Notice that for one problem instance, the results may differ in each run due to the
@@
 \caption{general schema for genetic algorithms}
-\label{fig:t2}
-\end{figure}
+\label{tbl:t2}
+\end{table}
 
@@
 larger problem size, The same experiments were performed for larger graphs
-The results in table~\ref{fig:t3}
-and table~\ref{fig:t4} correspond to the second test set, which consists of
+The results in table~\ref{tbl:t3}
+and table~\ref{tbl:t4} correspond to the second test set, which consists of
 five random graphs of size $n = 200$ with different
@@
 The corresponding results obtained by the
-genetic algorithm are shown in table~\ref{fig:t3}, while the results
-from the vercov algorithm are presented in table~\ref{fig:t4}.
+genetic algorithm are shown in table~\ref{tbl:t3}, while the results
+from the vercov algorithm are presented in table~\ref{tbl:t4}.
 See the previous paragraphs for a better understanding of these results.
 
-\begin{figure}[!htbp]
+\begin{table}[!htbp]
 \centering
@@
 \caption{general schema for genetic algorithms}
-\label{fig:t3}
-\end{figure}
+\label{tbl:t3}
+\end{table}
 
-\begin{figure}[!htbp]
+\begin{table}[!htbp]
 \centering
@@
 \caption{general schema for genetic algorithms}
-\label{fig:t4}
-\end{figure}
+\label{tbl:t4}
+\end{table}
 

### 2018-02-25 paper.tex
will start first iteration

@@
 \usepackage{caption}
+\usepackage{setspace}
 
@@
 \begin{center}
-\begin{align*}
-\text{Author: }					& \textit{Farouk Hjabo} \\
-\text{Academic Supervisor: }	& \textit{Dr. Said Desouki} \\
-\text{General Supervisor: }		& \textit{Dr. Kadan Aljoumaa} \\
-\text{Langauge Supervisor: }	& \textit{Mr. Fahmi Alammareen} \\
-\end{align*}
+\begin{onehalfspacing}
+
+\begin{tabular}{r l}
+Author:					&	\textit{Farouk Hjabo} \\
+Academic Supervisor:	&	\textit{Dr. Said Desouki} \\
+General Supervisor:		&	\textit{Dr. Kadan Aljoumaa} \\
+Langauge Supervisor:	&	\textit{Mr. Fahmi Alammareen} \\
+\end{tabular}
+
+\end{onehalfspacing}
 \end{center}
@@
 \phantomsection\addcontentsline{toc}{section}{List of Tables}
-\section*{abbrevs}  % Set the left side page header to "Abbreviations"
-\begin{center}
-\begin{tabular}{ l c } 
- GA & Genetic Algorithm \\ 
- cell4 & cell5 \\ 
- cell7 & cell8
+\section*{Abbreviations}  % Set the left side page header to "Abbreviations"
+\begin{onehalfspacing}
+\begin{tabular}{l l}
+
+\indent
+GA		&	\textbf{G}enetic \textbf{A}lgorithm \\
+
+\indent
+mvc		&	\textbf{M}inimum \textbf{V}ertex \textbf{C}over \\
+
+\indent
+mvcp	&	\textbf{M}inimum \textbf{V}ertex \textbf{C}over \textbf{P}roblem \\
+
 \end{tabular}
-\end{center}
+\end{onehalfspacing}
 
@@
 evidence that genetic algorithms can yield good solutions for a wide range of hard combinatorial optimization problems for which solutions can be represented by
-binary strings.
+binary strings. \cite{mvcp-back}
 

### 2018-02-25 paper.tex
fuck. line from paper.tex was deleted by mistake. good thing i noticed.

@@
 \ExecuteBibliographyOptions{
-	giveninits=true,
+	giveninits=false,
 	isbn=false,
@@
 \setlength{\parskip}{1em}
-\newcommand{\textem}[1]{\textbf{\textit{#1}}}
+\newcommand{\textem}[1]{\textbf{\emph{#1}}}
 \newtheorem{lemma}{Lemma}
@@
 \algrenewtext{For}[3]%
+{\algorithmicfor\ #1 = #2 \algorithmicto\ #3 \algorithmicdo}
 
@@
 \setlength{\parskip}{0em}
-\rm --- Charles Darwin
+--- Charles Darwin
 \end{flushright}
@@
 % List of Figures and Tables
-\cleardoublepage\phantomsection\addcontentsline{toc}{section}{List of Figures}
+\cleardoublepage\phantomsection\addcontentsline{toc}{subsection}{List of Figures}
 \listoffigures
 
-\phantomsection\addcontentsline{toc}{section}{List of Tables}
+\phantomsection\addcontentsline{toc}{subsection}{List of Tables}
 \listoftables
 
-\phantomsection\addcontentsline{toc}{section}{List of Tables}
+\phantomsection\addcontentsline{toc}{subsection}{Abbreviations}
 \section*{Abbreviations}  % Set the left side page header to "Abbreviations"
@@
 \subsection{The Intuition Behind GAs}
-Genetic Algorithms (GAs)~\cite{goldberg1989genetic} are population based
+Genetic Algorithms (GAs) \cite{coley, goldberg} are population based
 search algorithms, where by repeated use of genetic operations,
@@
 Successive new generations of better populations in the direction of
-search objectives are created. They are inspired by Darwinian principles
-based on natural evolution. In other words, the main idea behind genetic
-algorithms is that only the \textem{fittest} individuals will survive.\\
+search objectives are created.
+They are inspired by Darwinian principles
+based on natural evolution.
+In other words, the main idea behind genetic
+algorithms is that only the \textem{fittest} individuals will survive
+among generations of evolution.
+
 Main advantage of genetic algorithms is that they ideally do not make
@@
 operations research, robotics, social sciences, physics, politics, chemistry,
-etc...
+etc... \cite[ch.~6]{coley}
 
 \noindent
-So what is a GA? A typical GA consists of the following:
+So what is a GA? A typical GA consists of the following~\cite[ch.~1]{coley}:
 \vspace{-5mm}
@@
 \setlength{\parskip}{0em}
-\item a number, or \textem{population}, of candidate solutions to the problem.
-\item a way of calculating how good or bad the individual solutions within the
-population are. i.e. how \textem{fit} an individual is?
-\item a method for mixing fragments of the better solutions to form new, on
-average even better solutions. Which permits the population to \textem{evolve} naturally.
-\item a \textem{mutation} operator to avoid permanent loss of diversity within the
-solutions. This allows introducing new information in the population.
+
+\item
+a number, or \textem{population}, of candidate solutions to the problem.
+
+\item
+a way of calculating how good or bad the individual solutions within the
+population are.
+i.e. how \textem{fit} an individual is?
+
+\item
+a method for mixing fragments of the better solutions to form new, on
+average even better solutions.
+Which permits the population to \textem{evolve} naturally.
+
+\item
+a \textem{mutation} operator to avoid permanent loss of diversity within the
+solutions.
+This allows introducing new information in the population.
+
 \end{enumerate}
@@
 $ \vec{x} = ( x_1, \dots, x_n ) \in \{0, 1\}^n $
-of fixed length $n$. The fitness function
+of fixed length $n$.
+The fitness function
 $ f: \{0, 1\}^n \rightarrow \mathbb{R} $
@@
 the search towards regions of the search space where the
-average fitness of the population increases. The recombination operator
-allows for the exchange of information between different individuals, and
-mutation introduces innovation into the population. \\
+average fitness of the population increases.
+The recombination operator
+allows for the exchange of information between different individuals,
+and mutation introduces innovation into the population.
 This cycle is repeated until a termination criterion is fulfilled.
@@
 iterations of the basic cycle or when a satisfactory fitness
-level has been reached.
-refer to figure~\ref{fig:ga} for a visual representation of this process.
+level has been reached.\\
+Refer to figure~\ref{fig:ga} for a visual representation of this process,
+and refer to algorithm~\ref{alg:ga} for a more concise description.
 
@@
 \includegraphics[width=1\textwidth]{ga}
-\caption{general schema for genetic algorithms}
+\caption{General schema for genetic algorithms}
 \label{fig:ga}
@@
 f \left( \vec{x_i} \right) / \sum_{j=1}^uf \left( \vec{x_j} \right) $
-to serve as selection probabilities
-($u$ denotes the population size). This selection operator
-is called proportional selection. If the problem under
-consideration is a minimization one, or if the fitness
-function can take negative values, then $ f \left( \vec{x_i} \right) $ has to be
+to serve as selection probabilities ($u$ denotes the population size).
+This selection operator is called proportional selection.
+It is commonly used; as intuitively the more fit a solution is the more we
+want it to affect the next generations.\\
+If the problem under consideration is a minimization one,
+or if the fitness function can take negative values,
+then $ f \left( \vec{x_i} \right) $ has to be
 linearly transformed before calculating selection probabilities.
 This technique known as linear dynamic scaling is commonly used
-in genetic algorithms (see [13], pp. 123-124, or [14]).
+in genetic algorithms \cite[pp.~123--124]{goldberg}.
 
@@
 The recombination (crossover) operator allows for the
-exchange of information between different individuals. The
-original one-point crossover [9] works on two parent individuals
-(which are randomly chosen from the population, see the previous paragraph todo)
+exchange of information between different individuals.
+The original one-point crossover \cite{holland} works on two parent individuals
 by choosing a crossover point $ \chi \in \{1, \dots, n-1 \} $
 at random and exchanging all bits after the $ \chi^{\text{th}} $ one
-between both individuals. The crossover rate
-$ p_c \ (\text{e.g. } p_c \approx 0.6) $
-determines the probability to undergo crossover (see todo for more details).
+between both individuals.
+Therefore, two new off-springs will be formed.\\
+For example, if the two parents were encoded as $(111, 000)$ and we chose $\chi = 2$
+then the new two off-springs will be $(110, 001)$.
+The crossover rate $ p_c \ (\text{e.g. } p_c \approx 0.6) $
+determines the probability to undergo crossover (see algorithm~\ref{alg:ga} line~\ref{alg:crossover}),
+this allows the two parents to be present in the next generation; as crossover is not mandatory.
+Moreover, the value of $p_c$ indicates the ratio of new off-springs in the next generation.\\
 The crossover operator can be extended to a generalized
-multi-point crossover [10] or even to uniform crossover,
-where an it is randomly decided for each bit
-whether to exchange it or not [19]. The strong mixing effect
-introduced by uniform crossover is sometimes helpful
-to overcome local optima.
+multi-point crossover or even to uniform crossover,
+where it is randomly decided for each bit
+whether to exchange it or not.
+The strong mixing effect introduced by uniform crossover
+is sometimes helpful to overcome local optima.
 
 \paragraph{Mutation}
-Innovation, i.e. new information, is introduced into the
+Innovation (new information) is introduced into the
 population by means of mutation, which works by inverting
-bits with a small probability
-$ p_m \ (\text{e.g. } p_m \approx 0.001) $
+bits with a small probability $p_m \ (\text{e.g. } p_m \approx 0.001)$
+(see algorithm~\ref{alg:ga} lines~\ref{alg:m1}~\ref{alg:m2} for clarity).
 Though mutation is often interpreted as a rather unimportant operator
-in genetic algorithms [9], recent theoretical
+in genetic algorithms \cite{holland}, recent theoretical
 work gives strong evidence for an appropriate choice of a
-mutation rate $ p_m = 1/n $ on many problems [2; 12].
+mutation rate $ p_m = 1/n $ on many problems tocite{2, 12 misp}.
 
-For better understanding of figure~\ref{fig:ga}
 \begin{algorithm}
-\caption{Gentic Algorithm$\left( n, u, p_c, p_m, f \right)$}
+\caption{GenticAlgorithm$\left( n, u, p_c, p_m, f \right)$}
 \label{alg:ga}
@@
 \Comment{crossover}
+\label{alg:crossover}
 \State for each bit in $x$ flip it with probability $p_m$
 \Comment{mutation}
+\label{alg:m1}
 \State for each bit in $y$ flip it with probability $p_m$
 \Comment{mutation}
+\label{alg:m2}
 \State add $x, y$ to $Q$
@@
 optimization problem in computer science and is a typical
-example of an NP-hard optimization problem that has an
-approximation algorithm.
+example of an NP-complete optimization problem tocite{wolfram}
+that has approximation algorithms.
 The mvcp of an undirected graph $G = (V, E)$ where $V$ is
-the set of vertices and $E$ denotes the set of edges, consists
-in finding the smallest subset $V' \subseteq V$ such that
+the set of vertices and $E$ denotes the set of edges,
+consists in finding the smallest subset $V' \subseteq V$ such that
 $\forall \langle i, j \rangle \in E$, we have $i \in V'$ or $j \in V'$ (or both).
-$V'$ is said to be a vertex cover of $G$. The following is a formal definition of
+$V'$ is said to be a vertex cover of $G$.
+
+The following is a formal definition of
 the mvcp in which we make use of Stinson's terminology
-for combinatorial optimization problems [14]:
+for combinatorial optimization problems tocite{14 mvcp}:
 
@@
 is the set of vertices and $E \subseteq V \times V$ the
-set of edges. An edge between vertices $i, j$ is denoted
-by the pair $\langle i, j \rangle \in E$. We define the adjacency
-matrix $e_{ij}$ according to:
+set of edges.
+An edge between vertices $i, j$ is denoted
+by the pair $\langle i, j \rangle \in E$.
+We define the adjacency matrix $e_{ij}$ according to:
 \[
@@
 \]
-especially, we have $e_{ii} = 0$
+On particular, we have $e_{ii} = 0$.
 
@@
 
-an interesting property of the mvcp is that by
+An interesting property of the mvcp is that by
 solving it, we also have a solution for two other
-graph problems: the \textit{maximum independent set problem}%
-\footnote{%
-misp: given $G = (V, E)$, find the largest subset $V' \subseteq V$
-such that $\forall i, j \in V', \langle i, j \rangle \notin E$
-}
-and the \textit{maximum clique problem}%
-\footnote{%
-mcp: given $G = (V, E)$, find the largest subset $V' \subseteq V$
-such that $\forall i, j \in V', \langle i, j \rangle \in E$
-}
-The close relationship between these problems
-is characterized by the following lemma [6].
-
+graph problems: the \textit{maximum independent set problem}
+(given $G = (V, E)$, find the largest subset $V' \subseteq V$
+such that $\forall i, j \in V', \langle i, j \rangle \notin E$)
+and the \textit{maximum clique problem}
+(given $G = (V, E)$, find the largest subset $V' \subseteq V$
+such that $\forall i, j \in V', \langle i, j \rangle \in E$)
+The close relationship between these problems is characterized
+by the following lemma tocite{6 misp}.
 \begin{lemma}
@@
 \item $V - V'$ is the maximum independent set in $G$.
-\item $V - V'$ is the maximum clique in $\bar{G} = (V, \bar{E})$, where \\
+\item $V - V'$ is the maximum clique in $\bar{G} = (V, \bar{E})$,\\[1mm]
+where
 $\bar{E}=\left\{ \langle i, j \rangle\in V \times V :
@@
 \end{lemma}
+
 Consequently, one can obtain a solution of the maximum independent set
@@
 be tempted to use a greedy-based heuristic to tackle the
-mvcp. The algorithm consists in repeatedly selecting a
+mvcp.
+The algorithm consists in repeatedly selecting a
 vertex of highest degree (the node that covers as many
 of the remaining edges as possible), and removing all
-of its incident edges. This is not a good strategy as
-was demonstrated by Papadimitriou and Steiglitz ([10],
-p. 407). \\
-They considered regular graphs, each of which
-consists of three levels. The first two levels have the same
+of its incident edges.
+This is not a good strategy as was demonstrated
+by Papadimitriou and Steiglitz tocite{10 p. 407 mvcp}.
+
+They considered regular graphs\footnote{%
+by regular graphs we don't refer to the definition where
+each vertex has the same degree.
+}, each of which consists of three levels.
+The first two levels have the same
 number of nodes while the third level has two nodes less
 than the number of nodes found on the previous two
-levels. More precisely, each graph consists of $n = 3k + 4 (k \geq 1)$
+levels.
+More precisely, each graph consists of $n = 3k + 4 \ (k \geq 1)$
 nodes; $k+2$ nodes on the first level, labeled $1, 2, \dots, k+2$;
@@
 the optimal solution has size $k + 2$.
+
 However this algorithm is not totally useless. It may be shown that it always
@@
 That is, if $C^*(n)$ is the size of the optimal
-solution and $C(n)$ is the size of the solution found by the aforementioned
-algorithm. Then we have $\frac{C(n)}{C^*(n)} = \Theta(\lg n)$ [9], p-323.
+solution and $C(n)$ is the size of the solution found by the greedy
+algorithm. Then we have $\frac{C(n)}{C^*(n)} = \Theta(\lg n)$ tocite{9 p. 323 mvc}.
 
@@
 \centering
-\includegraphics[width=1\textwidth]{ps}
-\caption{Construction of the regular graph after Papadimitriou
+\includegraphics[width=0.5\textwidth]{ps}
+\caption[The regular graph after Papadimitriou
+and Steiglitz]{Construction of the regular graph after Papadimitriou
 and Steiglitz with $k=3$.}
@@
 The following simple algorithm is surprisingly the
-best approximation algorithm known for the mvcp ([9],
-p. 301).
+best approximation algorithm known for the mvcp
+tocite{9 p.~301 mvcp}.
 
@@
 it returns is guaranteed to be no more than twice the
-size of an optimal vertex cover ([1], p. 968).
+size of an optimal vertex cover tocite{[1], p. 968 mvcp}.
 More precisely, if $C^*$ is the size of the optimal
@@
 then the inequality $C \leq 2C^*$ must hold (notice that here the approximation
-doesn't depend on the number of vertices $n$).
+doesn't depend on the number of vertices).
 
@@
 \label{sec:GAmvcp}
-In order to apply GA to solve the mvcp, a cover $V'$ is represented
+In order to apply genetic algorithm to solve the mvcp, a cover $V'$ is represented
 by a binary vector $\vec{x} = x_1x_2 \dots x_n$ where $x_i = 1$ if
@@
 Using this representation, genetic algorithm is applied to minimize the following
-fitness function: [0] \\
+fitness function~\cite{mvcp-back}:
 \begin{equation}
@@
 \end{equation}
+
 The term $ \sum_{i=1}^{n} x_i $ of $ f(\vec{x}) $ determines the size of the
@@
 Consequently, any infeasible solution will have a fitness greater than
-or equal to $n$, and for any feasible solution the second term will
-drop to zero.
+or equal to $n$. And for any feasible solution the second term will
+drop to zero, making the fitness value of the worst feasible solution at most $n$.
+
 This fitness function was developed according to the
 following design principles that are important for a
-successful penalty function approach [11 $||$ 13 $||$ 7]:
-
+successful penalty function approach tocite{7,11 mvcp}:
 \begin{itemize}
-\vspace{-3mm}
+\vspace{-4mm}
 
@@
 by using a genetic algorithm with a population size of
-$u = 50$, a mutation rate $p_m = 1/n$, crossover rate
-$p_c = 0.6$, proportional selection, and two-point crossover.
-As reported in [2, 12], the latter is expected to perform
+$u = 50$, mutation rate $p_m = 1/n$, crossover rate
+$p_c = 0.6$, proportional selection, and two-point crossover \cite{mvcp-back}.
+As reported in tocite{2, 12 mvcp}, the latter is expected to perform
 better than the traditional one-point crossover.
-The termination criterion is specified in section~\ref{sec:er}.
+A bound for the total number
+of fitness function evaluations is set as the termination
+criterion, see section~\ref{sec:er} for details.
 
@@
 For the experimental tests,
-the genetic algorithm software package GENEsYs is used [1]misp.
-This implementation is based on the widely used GENESIS software by Grefenstette
-(see [3], pp. 374-377 misp), but allows for more 
-flexibility concerning genetic operators and data monitoring.
-The parameter settings for our experiments are
+the genetic algorithm software package GENEsYs is used tocite{[1] misp}.
+This implementation is based on the widely used GENESIS software by Grefenstette tocite{3, pp. 374-377 misp},
+but allows for more  flexibility concerning genetic operators and data monitoring.
+The parameter settings for the experiments are
 given in section~\ref{sec:GAmvcp}.
 
-Multiple problem instances are used to demonstrate the applicability of GAs to tackle the mvcp
+\paragraph{Test Set 1:}
+Multiple problem instances are used to demonstrate the applicability of GAs to tackle the mvcp.
 The results in table~\ref{tbl:t1}
@@
 five random graphs of size $n = 100$ with different
-edge densities $d$, $d \in \{0.1, 0.2, 0.3, 0.4, 0.5\}$, are used.
+edge densities $d$.
+Densities $d \in \{0.1, 0.2, 0.3, 0.4, 0.5\}$ are used respectively.
 An edge density of $d = 0.1$ means that an edge is placed between two
 nodes with a probability of 0.1.
-Moreover we construct the graphs in a way that guarantees an optimum of quality 55
-(we set $k = 55$ in algorithm~\ref{alg:gen}).
-In addition to the regular graphs introduced by
-Papadimitriou and Steiglitz and described in section~\ref{sec:ra}.
-Recall that these graphs contain $n=3k+4 (k \geq 1)$ nodes distributed on three levels.
+Moreover, we construct the graphs in a way that guarantees an optimum of quality 55 \cite{mvcp-back}.
+i.e. we use algorithm~\ref{alg:gen} with $k = 55$ to generate random graphs.
+In addition, the regular graphs introduced by
+Papadimitriou and Steiglitz and described in section~\ref{sec:ra} are used.
+Recall that these graphs contain $n=3k+4 \ (k \geq 1)$ nodes distributed on three levels.
 They can be scaled up by choosing high values for $k$.
-A graph instance of the regular graph of size $n = 100 (k=32)$ is chosen.
+A graph instance of the regular graph of size $n = 100 \  (k=32)$ is chosen.
 
 \begin{algorithm}
-\caption{Generate$(n, d, k)$}
+\caption{GenerateRandomGraph$(n, d, k)$}
 \label{alg:gen}
@@
 evidence that genetic algorithms can yield good solutions for a wide range of hard combinatorial optimization problems for which solutions can be represented by
-binary strings. \cite{mvcp-back}
+binary strings. \cite[p.~400, p.]{mvcp-back, goldberg} \cite{coley}
 

### 2018-02-25 paper.tex
going to school

@@
 \subsection{GA for the mvcp}
+\section{Experiments}
 \label{sec:GAmvcp}
@@
 
-\section{Experimental Results}
+\subsection{Experimental Results}
 \label{sec:er}
@@
 The results in table~\ref{tbl:t1}
-and table~\ref{tbl:t2} correspond to the first test set, which consists of
+and table~\ref{tbl:t2} correspond to the test set 1, which consists of
 five random graphs of size $n = 100$ with different
@@
 Moreover, we construct the graphs in a way that guarantees an optimum of quality 55 \cite{mvcp-back}.
-i.e. we use algorithm~\ref{alg:gen} with $k = 55$ to generate random graphs.
+i.e. we use algorithm~\ref{alg:gen} with $k = 55$ to generate random graphs.\\
 In addition, the regular graphs introduced by
@@
 
-For each of these graphs, a total of
+\paragraph{Termination:}
+As a termination criterion for the genetic algorithm,
+a bound for the total number of fitness function evaluations is set.
+For example The total number of function evaluations per single run
+is chosen to be $2 \cdot 10^4$ in table~\ref{tbl:t1}.
+That is, the algorithm terminates when $2 \cdot 10^4$ evaluations of the fitness function
+had occurred.
+This bound is indicated as an index $t$ in the notation $f_t(\vec{x})$.
+Consequently, only a small fraction of the search space is explored by the genetic algorithm.
+This fraction is about
+$ 2 \cdot 10^4 / 2^{100} \approx 1.6 \cdot 10^{-24} \% $
+for test set 1.
+And it is about $ 4 \cdot 10^4 / 2^{200} \approx 2.5 \cdot 10^{-54} \% $ for test set 2.
+
+\paragraph{Table~\ref{tbl:t1}:}
+For each graph in test set 1, a total of
 $N = 100$ independent runs of the genetic algorithm is performed.
@@
 Furthermore, the average fitness value $\bar{f}$ over
-all 100 runs is indicated at the bottom of the table.
+all 100 runs is indicated at the bottom of the table.\\
 For example, the first column in table~\ref{tbl:t1} indicates
@@
 the best obtained fitness values over the 100 runs.
-
-As a termination criterion for the genetic algorithm, a bound for the total number of function evaluations is set.
-For example The total number of function evaluations per single run is chosen to be $2 \cdot 10^4$ in table~\ref{tbl:t1}.
-That is, the algorithm terminates when $2 \cdot 10^4$ evaluations of the fitness function
-had occurred.
-This bound is indicated as an index $t$ in the notation $f_t(\vec{x})$.
-Consequently, only a small fraction of the search space is explored by the genetic algorithm.
-This fraction is about $ 2 \cdot 10^4 / 2^{100} \approx 1.6 \cdot 10^{-24} \% $ for the first test set.
-and it is about $ 4 \cdot 10^4 / 2^{200} \approx 2.5 \cdot 10^{-54} \% $ for the second test set.
 
@@
 
-For each of the problems in the first test set, a total of $N=100$
-independent runs of the vercov algorithm is performed. The results are summarized in table~\ref{tbl:t2}.
+\paragraph{Table~\ref{tbl:t2}:}
+For each of the problems in the test set 1, a total of $N=100$
+independent runs of the vercov algorithm is performed.
+The results are summarized in table~\ref{tbl:t2}.
 Notice that for one problem instance, the results may differ in each run due to the
@@
 
+\paragraph{Test Set 2:}
 To test the behaviour of the genetic algorithm
 as well as the vercov algorithm for an even
-larger problem size, The same experiments were performed for larger graphs
+larger problem size, The same experiments
+were performed for larger graphs.
 The results in table~\ref{tbl:t3}
-and table~\ref{tbl:t4} correspond to the second test set, which consists of
-five random graphs of size $n = 200$ with different
-edge densities $d$, $d \in \{0.1, 0.2, 0.3, 0.4, 0.5\}$, are used.
-Moreover we construct the graphs in a way that guarantees an optimum of quality 110
-(see algorithm~\ref{alg:gen}).
+and table~\ref{tbl:t4} correspond to test set 2,
+which consists of five random graphs of size
+$n = 200$ with different edge densities $d$.
+Densities $d \in \{0.1, 0.2, 0.3, 0.4, 0.5\}$ are used.
+Moreover, we construct the graphs in a way that guarantees an optimum of quality 110
+(see algorithm~\ref{alg:gen}, we set $k = 110$).
 In addition to a graph instance of the regular graphs introduced by
-Papadimitriou and Steiglitzof of size $n = 220 (k=66)$.
+Papadimitriou and Steiglitzof of size $n = 220 \ (k=66)$.
 In this case, the genetic algorithm
-was allowed to run for $4 \cdot 10^4$ function evaluations.
+was allowed to run for $4 \cdot 10^4$ function evaluations.\\
 The corresponding results obtained by the
 genetic algorithm are shown in table~\ref{tbl:t3}, while the results
-from the vercov algorithm are presented in table~\ref{tbl:t4}.
+from the vercov algorithm are shown in table~\ref{tbl:t4}.
 See the previous paragraphs for a better understanding of these results.
@@
 
-\subsection{results comments}
+% herereh
+\subsection{Experimental Conclusions}
 From these tables, a number of interesting conclusions

### 2018-02-26 paper.tex
some weird error in texmaker

@@
 {\algorithmicfor\ #1 = #2 \algorithmicto\ #3 \algorithmicdo}
+\captionsetup{font=footnotesize}
 
@@
 \begin{center}
-Keywords: genetic algorithms, NP-complete, combinatorial optimization, non-deterministic algorithms, approximation algorithms, minimum vertex cover.
+Keywords: minimum vertex cover, NP-complete, genetic algorithms,\\
+combinatorial optimization, approximation algorithms.
 \end{center}
@@
 They considered regular graphs\footnote{%
-by regular graphs we don't refer to the definition where
+by ``regular graphs'' we don't refer to the definition where
 each vertex has the same degree.
@@
 \includegraphics[width=1\textwidth]{t1}
-\caption{general schema for genetic algorithms}
+\caption{%
+Experimental results obtained by the genetic algorithm for five random graphs of size $n = 100$ with edge density: $d = 0.1$ (``mvcp100-01''), $d = 0.2$ (``mvcp100-02''), $d = 0.3$ (``mvcp100-03''), $d = 0.5$ (``mvcp100-04''), $d = 0.5$ (``mvcp100-05'') and the regular graph of size $n = 100 \ (k=32)$ from Papadimitriou and Steiglitz (``PS100'').%
+}
 \label{tbl:t1}
@@
 \includegraphics[width=1\textwidth]{t2}
-\caption{general schema for genetic algorithms}
+\caption{%
+Experimental results obtained by the vercov algorithm for five random graphs of size $n = 100$ with edge density: $d = 0.1$ (``mvcp100-01''), $d = 0.2$ (``mvcp100-02''), $d = 0.3$ (``mvcp100-03''), $d = 0.5$ (``mvcp100-04''), $d = 0.5$ (``mvcp100-05'') and the regular graph of size $n = 100 \ (k=32)$ from Papadimitriou and Steiglitz (``PS100'').%
+}
 \label{tbl:t2}
@@
 \includegraphics[width=1\textwidth]{t3}
-\caption{general schema for genetic algorithms}
+\caption{%
+Experimental results obtained by the genetic algorithm for five random graphs of size $n = 200$ with edge density: $d = 0.1$ (``mvcp200-01''), $d = 0.2$ (``mvcp200-02''), $d = 0.3$ (``mvcp200-03''), $d = 0.5$ (``mvcp200-04''), $d = 0.5$ (``mvcp200-05'') and the regular graph of size $n = 202 \ (k=66)$ from Papadimitriou and Steiglitz (``PS202'').%
+}
 \label{tbl:t3}
@@
 \includegraphics[width=1\textwidth]{t4}
-\caption{general schema for genetic algorithms}
+\caption{%
+Experimental results obtained by the vercov algorithm for five random graphs of size $n = 200$ with edge density: $d = 0.1$ (``mvcp200-01''), $d = 0.2$ (``mvcp200-02''), $d = 0.3$ (``mvcp200-03''), $d = 0.5$ (``mvcp200-04''), $d = 0.5$ (``mvcp200-05'') and the regular graph of size $n = 202 \ (k=66)$ from Papadimitriou and Steiglitz (``PS202'').%
+}
 \label{tbl:t4}
@@
 
-% herereh
 \subsection{Experimental Conclusions}
 From these tables, a number of interesting conclusions
-can be drawn. For the random graphs used to compare the
+can be drawn.
+For the random graphs used to compare the
 genetic algorithm and the vercov algorithm,
-it is known by construction that an optimum of quality 55 exists in the first test set,
-(respectively, an optimum of quality 110 exists for the second test set). This optimum is likely to be the
-global optimum, And it is found by the genetic
-algorithm at least once within the $N = 100$ runs that were performed.
+it is known by construction that an optimum of
+quality 55 exists for test set 1,
+(respectively, an optimum of quality 110 exists
+for the test set 2).
+This optimum is likely to be the global optimum.
+And it is found by the genetic algorithm at least once
+within the $N = 100$ runs that were performed.
 
@@
 become simpler for the genetic algorithm when the edge
-density is increased. For an edge density of $d \in \{0.4, 0.5\}$, the
+density is increased.
+For an edge density of $d \in \{0.4, 0.5\}$, the
 genetic algorithm almost surely finds the global optimum
-of the problems, while vercov algorithm gives a relatively terrible results.
+of the problems, while vercov algorithm gives
+a relatively terrible results.
 
@@
 runs identify a solution of quality $2k + 2$.
-Whereas, vercov algorithm gives a solution of quality $2k + 2$ in all of the 100 runs as expected.
+Whereas, vercov algorithm gives a solution of
+quality $2k + 2$ in all of the 100 runs as expected tocite{[10] mvcp}.
 Recall that the graphs are constructed
@@
 of quality $2k + 2$.
-The random choice of edges in line~\ref{alg:rand} of the algorithm implies that nodes from either layers one and two, or layers two and three are involved in the solution being constructed, which in turn implies that two layers have to be part of the solution found by the algorithm [10]mvcp.
+The random choice of edges (line~\ref{alg:rand} of algorithm~\ref{alg:vercov})
+implies that nodes from either layers one and two, or layers two and three
+are involved in the solution being constructed,
+which in turn implies that two layers have to be part of the solution
+found by the algorithm.
 
-For the randomly constructed graphs, the vercov algorithm performs
-poorly.
-It barely finds solutions of quality 80 (for graphs of size 100) and 172 (for graphs of size 200).
+For the randomly constructed graphs, the vercov algorithm
+performs poorly.
+It barely finds solutions of quality 80 (for graphs of size 100)
+and 172 (for graphs of size 200).
 The average performance of the vercov algorithm (surprisingly)
-decreases as the edge density is increased.
+decreases as the edge density is increased;
 i.e. the problems become even harder for the vercov algorithm
@@
 One can demonstrate this by calculating
-the ratio of the absolute (or equivalently the relative) error.
+the ratio of the absolute (or equivalently, the relative) error.
 For example, for the first problem instance,
@@
 \section{Conclusion}
-In this work, we have demonstrated that genetic algorithms can be used in a straightforward way t
-good approximate solutions of the minimum vertex cover
-problem. Moreover, the results found by the genetic algorithm are better than those obtained from the best
-known traditional heuristic, the vercov algorithm. These, in addition to other good results obtained on, highly constrained combinatorial optimization
-problems such as the subset sum [7], minimum tardy
-task [7], and multiple knapsack problems [8], give strong
-evidence that genetic algorithms can yield good solutions for a wide range of hard combinatorial optimization problems for which solutions can be represented by
-binary strings. \cite[p.~400, p.]{mvcp-back, goldberg} \cite{coley}
+Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
+tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
+quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
+consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
+cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
+proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 

### 2018-02-26 paper.tex
will finish references

@@
 \usepackage[autostyle]{csquotes}
-\usepackage[]{biblatex}
+\usepackage{biblatex}
 \usepackage{amsfonts}
@@
 \subsection{GA for the mvcp}
-\section{Experiments}
 \label{sec:GAmvcp}
@@
 
-\subsection{Experimental Results}
-\label{sec:er}
+\section{Experiments}
 For the experimental tests,
@@
 given in section~\ref{sec:GAmvcp}.
+
+\subsection{Experimental Results}
+\label{sec:er}
+The results given within the tables are explicitly provided
+from~\cite{mvcp-back} with no modification or any sort of validation.
 

### 2018-02-26 paper.tex
finished references.bib

--- 2018-02-26 paper.tex
@@
 \ExecuteBibliographyOptions{
-	giveninits=false,
-	isbn=false,
-	doi=false,
-	url=false
+	giveninits = true,
+	isbn = false,
+	maxbibnames = 99,
+	url = false
 }
@@
 work gives strong evidence for an appropriate choice of a
-mutation rate $ p_m = 1/n $ on many problems tocite{2, 12 misp}.
+mutation rate $ p_m = 1/n $ on many problems \cite{2:misp, 12:misp}.
 
@@
 optimization problem in computer science and is a typical
-example of an NP-complete optimization problem tocite{wolfram}
+example of an NP-complete optimization problem \cite{wolfram:mvc}
 that has approximation algorithms.
@@
 the mvcp in which we make use of Stinson's terminology
-for combinatorial optimization problems tocite{14 mvcp}:
+for combinatorial optimization problems~\cite{14:mvcp}:
 
@@
 The close relationship between these problems is characterized
-by the following lemma tocite{6 misp}.
+by the following lemma \cite{6:misp}.
 \begin{lemma}
@@
 This is not a good strategy as was demonstrated
-by Papadimitriou and Steiglitz tocite{10 p. 407 mvcp}.
+by Papadimitriou and Steiglitz \cite[p.~407]{10:mvcp}.
 
@@
 \exists \alpha, \beta, n_0 : \forall n \geq n_0, \ 
-\alpha \cdot g(n) \leq f(n) \leq \beta \cdot g(n)
-$},
+\alpha \cdot g(n) \leq f(n) \leq \beta \cdot g(n)$ \cite[pp.~41--43]{cormen}},
 where $n$ is the number of vertices.
@@
 solution and $C(n)$ is the size of the solution found by the greedy
-algorithm. Then we have $\frac{C(n)}{C^*(n)} = \Theta(\lg n)$ tocite{9 p. 323 mvc}.
+algorithm. Then we have $\frac{C(n)}{C^*(n)} = \Theta(\lg n)$ \cite[p.~323]{9:mvcp}.
 
@@
 The following simple algorithm is surprisingly the
-best approximation algorithm known for the mvcp
-tocite{9 p.~301 mvcp}.
+best approximation algorithm known for the mvcp \cite[p.~301]{9:mvcp}.
 
@@
 it returns is guaranteed to be no more than twice the
-size of an optimal vertex cover tocite{[1], p. 968 mvcp}.
+size of an optimal vertex cover \cite[p.~968]{cormen}.
 More precisely, if $C^*$ is the size of the optimal
@@
 following design principles that are important for a
-successful penalty function approach tocite{7,11 mvcp}:
+successful penalty function approach \cite{7:mvcp, 11:mvcp}:
 \begin{itemize}
@@
 $p_c = 0.6$, proportional selection, and two-point crossover \cite{mvcp-back}.
-As reported in tocite{2, 12 mvcp}, the latter is expected to perform
+As reported in \cite{2:mvcp, 12:mvcp}, the latter is expected to perform
 better than the traditional one-point crossover.
@@
 of fitness function evaluations is set as the termination
-criterion, see section~\ref{sec:er} for details.
+criterion \cite{mvcp-back}, see section~\ref{sec:er} for details.
 
-\subsection{Experimental Results}
-\label{sec:er}
+\section{Experiments}
 For the experimental tests,
-the genetic algorithm software package GENEsYs is used tocite{[1] misp}.
-This implementation is based on the widely used GENESIS software by Grefenstette tocite{3, pp. 374-377 misp},
+the genetic algorithm software package GENEsYs is used \cite{1:misp}.
+This implementation is based on the widely used GENESIS software by Grefenstette \cite{5:mvcp},
 but allows for more  flexibility concerning genetic operators and data monitoring.
@@
 
-\paragraph{Test Set 1:}
+\subsection{Experimental Results}
+\label{sec:er}
+
+\paragraph{Test set~1:}
 Multiple problem instances are used to demonstrate the applicability of GAs to tackle the mvcp.
 The results in table~\ref{tbl:t1}
-and table~\ref{tbl:t2} correspond to the test set 1, which consists of
+and table~\ref{tbl:t2} correspond to the test set~1, which consists of
 five random graphs of size $n = 100$ with different
@@
 $ 2 \cdot 10^4 / 2^{100} \approx 1.6 \cdot 10^{-24} \% $
-for test set 1.
-And it is about $ 4 \cdot 10^4 / 2^{200} \approx 2.5 \cdot 10^{-54} \% $ for test set 2.
+for test set~1.
+And it is about $ 4 \cdot 10^4 / 2^{200} \approx 2.5 \cdot 10^{-54} \% $ for test set~2.
 
 \paragraph{Table~\ref{tbl:t1}:}
-For each graph in test set 1, a total of
+For each graph in test set~1, a total of
 $N = 100$ independent runs of the genetic algorithm is performed.
@@
 \includegraphics[width=1\textwidth]{t1}
-\caption{%
+\caption[Results obtained by GA for graphs in test set~1]{%
 Experimental results obtained by the genetic algorithm for five random graphs of size $n = 100$ with edge density: $d = 0.1$ (``mvcp100-01''), $d = 0.2$ (``mvcp100-02''), $d = 0.3$ (``mvcp100-03''), $d = 0.5$ (``mvcp100-04''), $d = 0.5$ (``mvcp100-05'') and the regular graph of size $n = 100 \ (k=32)$ from Papadimitriou and Steiglitz (``PS100'').%
@@
 \paragraph{Table~\ref{tbl:t2}:}
-For each of the problems in the test set 1, a total of $N=100$
+For each of the problems in the test set~1, a total of $N=100$
 independent runs of the vercov algorithm is performed.
@@
 \includegraphics[width=1\textwidth]{t2}
-\caption{%
+\caption[Results obtained by vercov algorithm for graphs in test set~1]{%
 Experimental results obtained by the vercov algorithm for five random graphs of size $n = 100$ with edge density: $d = 0.1$ (``mvcp100-01''), $d = 0.2$ (``mvcp100-02''), $d = 0.3$ (``mvcp100-03''), $d = 0.5$ (``mvcp100-04''), $d = 0.5$ (``mvcp100-05'') and the regular graph of size $n = 100 \ (k=32)$ from Papadimitriou and Steiglitz (``PS100'').%
@@
 
-\paragraph{Test Set 2:}
+\paragraph{Test set~2:}
 To test the behaviour of the genetic algorithm
@@
 The results in table~\ref{tbl:t3}
-and table~\ref{tbl:t4} correspond to test set 2,
+and table~\ref{tbl:t4} correspond to test set~2,
 which consists of five random graphs of size
@@
 \includegraphics[width=1\textwidth]{t3}
-\caption{%
+\caption[Results obtained by GA for graphs in test set~2]{%
 Experimental results obtained by the genetic algorithm for five random graphs of size $n = 200$ with edge density: $d = 0.1$ (``mvcp200-01''), $d = 0.2$ (``mvcp200-02''), $d = 0.3$ (``mvcp200-03''), $d = 0.5$ (``mvcp200-04''), $d = 0.5$ (``mvcp200-05'') and the regular graph of size $n = 202 \ (k=66)$ from Papadimitriou and Steiglitz (``PS202'').%
@@
 \includegraphics[width=1\textwidth]{t4}
-\caption{%
+\caption[Results obtained by vercov algorithm for graphs in test set~2]{%
 Experimental results obtained by the vercov algorithm for five random graphs of size $n = 200$ with edge density: $d = 0.1$ (``mvcp200-01''), $d = 0.2$ (``mvcp200-02''), $d = 0.3$ (``mvcp200-03''), $d = 0.5$ (``mvcp200-04''), $d = 0.5$ (``mvcp200-05'') and the regular graph of size $n = 202 \ (k=66)$ from Papadimitriou and Steiglitz (``PS202'').%
@@
 it is known by construction that an optimum of
-quality 55 exists for test set 1,
+quality 55 exists for test set~1,
 (respectively, an optimum of quality 110 exists
-for the test set 2).
+for the test set~2).
 This optimum is likely to be the global optimum.
@@
 Whereas, vercov algorithm gives a solution of
-quality $2k + 2$ in all of the 100 runs as expected tocite{[10] mvcp}.
+quality $2k + 2$ in all of the 100 runs as expected \cite{10:mvcp}.
 Recall that the graphs are constructed
@@
 proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+\cite[hi][go]{coley} \cite{davis}
 

### 2018-02-28 paper.tex
done for today
done for almost everything

@@
 \usepackage{wrapfig}
-\usepackage[a4paper, total={6in, 8in}]{geometry}
-\usepackage{hyperref}
-\usepackage[all]{hypcap}
 \usepackage[autostyle]{csquotes}
@@
 \usepackage{amsfonts}
-\usepackage{algorithm}
 \usepackage[end]{algpseudocode}
@@
 \usepackage{setspace}
+\usepackage{hyperref}
+\usepackage[a4paper, total={6in, 8in}]{geometry}
+\usepackage{algorithm}
+\usepackage[all]{hypcap}
 
@@
 \pagenumbering{roman}
-\cleardoublepage\phantomsection\addcontentsline{toc}{section}{Cover Page}
+\phantomsection\addcontentsline{toc}{section}{Cover Page}
 
@@
 % abstract page
-\cleardoublepage\phantomsection\addcontentsline{toc}{section}{Abstract}
+\phantomsection\addcontentsline{toc}{section}{Abstract}
 
 \begin{abstract}
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
-tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
-quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
-consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
-cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
-proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Remarkable results obtained from the application of a
+genetic algorithm to the minimum vertex cover problem
+are reported, and tested against the results of the
+best known heuristic algorithm for graphs of sizes 100 and 200 nodes.
+In contrast to many other approximation algorithms that use problem-specific
+knowledge, the approach presented relies on a graded penalty term component
+of the fitness function to penalize infeasible solutions.
 \end{abstract}
@@
 % table of contents page
-\cleardoublepage\phantomsection\addcontentsline{toc}{section}{Contents}
+\setstretch{0.5}
+\phantomsection\addcontentsline{toc}{section}{Contents}
 \tableofcontents
+\setstretch{1.0}
+
 \pagebreak
@@
 % List of Figures and Tables
-\cleardoublepage\phantomsection\addcontentsline{toc}{subsection}{List of Figures}
+\phantomsection\addcontentsline{toc}{subsection}{List of Figures}
 \listoffigures
@@
 \section{Introduction}
+\label{sec:intro}
 Once the NP-hardness of a combinatorial optimization
 problem is established, the search for an optimal solution
-is abandoned. The goal then becomes one of finding a
-good heuristic, i.e. a polynomial running time algorithm
-that can find solutions close to the optimal. In most cases,
-traditional heuristics are problem dependent; a heuristic is
-tailored to the specific problem it is trying to solve.
+is abandoned.
+Our goal then becomes one of finding good heuristics
+for that problem.
+That is, we try to find approximation algorithms
+that have polynomial time complexities and return near-optimal
+solutions.
+In most cases, the heuristic is problem dependent; it is tailored to specific problem
+it is trying to solve, and it is tightly coupled with observations made about the problem.
+The \textit{minimum vertex cover} problem is a typical example of such
+problems \cite{wolfram:mvc}.
+Due to its numerous applications especially in various
+matching problems, the problem is not abandoned and it has many
+approximation algorithms.
 
-In this paper, we present an alternative approach that
-uses genetic algorithms as a generalized heuristic for solving NP-hard combinatorial optimization problems. The
-application of a genetic algorithm is demonstrated here for
-the \textit{minimum vertex cover} problem. These algorithms
-have been successfully applied to a broad range of problems. This wide range can be tackled by genetic algorithms
-mainly due to the fact that they work with an encoding of
-the domain rather than with the problem domain itself.
+In this work, we present an alternative approach that
+uses \textit{genetic algorithms} as a generalized heuristic for
+solving NP-hard combinatorial optimization problems.
+These algorithms have been successfully applied to a broad
+range of problems.
+This wide range can be tackled by genetic algorithms
+mainly due to the fact that these algorithms work with an
+encoding of the problem rather than the characteristics
+of that problem.
+Remarkable results were obtained and compared to the results of the
+best known heuristic algorithm for the mvcp.
+
+The outline of this paper is as follows: Firstly, Section~\ref{sec:ga} gives a
+short introduction to genetic algorithms, and explains briefly how they work.
+Section~\ref{sec:mvcp} introduces the mvcp with two of its main heuristics,
+and explains its representation for an application of the genetic algorithm.
+Lastly, Section~\ref{sec:exper} presents our experimental results and
+points out the notable observations that can be drawn from these results.
 
 \section{Genetic Algorithms}
+\label{sec:ga}
 \subsection{The Intuition Behind GAs}
@@
 Which permits the population to \textem{evolve} naturally.
-
-\item
-a \textem{mutation} operator to avoid permanent loss of diversity within the
-solutions.
-This allows introducing new information in the population.
 
@@
 
-\begin{algorithm}
+\begin{algorithm}[!htbp]
 \caption{GenticAlgorithm$\left( n, u, p_c, p_m, f \right)$}
@@
 \section{The Minimum Vertex Cover Problem}
+\label{sec:mvcp}
 The problem of finding a minimum vertex cover is a classical
@@
 \begin{lemma}
+\label{lem}
 \ \\[3mm]
@@
 \caption[The regular graph after Papadimitriou
-and Steiglitz]{Construction of the regular graph after Papadimitriou
-and Steiglitz with $k=3$.}
+and Steiglitz for $k=3$]
+{Construction of the regular graph after Papadimitriou
+and Steiglitz with $k=3$}
 \label{fig:ps}
@@
 
-\begin{algorithm}
+\begin{algorithm}[!htbp]
 \caption{vercov($G = (V, E)$)}
@@
 \section{Experiments}
+\label{sec:exper}
 For the experimental tests,
@@
 
-\begin{algorithm}
+\begin{algorithm}[!htbp]
 \caption{GenerateRandomGraph$(n, d, k)$}
@@
 For each of the problems in the test set~1, a total of $N=100$
-independent runs of the vercov algorithm is performed.
+independent runs of the vercov heuristic is performed.
 The results are summarized in table~\ref{tbl:t2}.
@@
 \includegraphics[width=1\textwidth]{t2}
-\caption[Results obtained by vercov algorithm for graphs in test set~1]{%
-Experimental results obtained by the vercov algorithm for five random graphs of size $n = 100$ with edge density: $d = 0.1$ (``mvcp100-01''), $d = 0.2$ (``mvcp100-02''), $d = 0.3$ (``mvcp100-03''), $d = 0.5$ (``mvcp100-04''), $d = 0.5$ (``mvcp100-05'') and the regular graph of size $n = 100 \ (k=32)$ from Papadimitriou and Steiglitz (``PS100'').%
+\caption[Results obtained by vercov heuristic for graphs in test set~1]{%
+Experimental results obtained by the vercov heuristic for five random graphs of size $n = 100$ with edge density: $d = 0.1$ (``mvcp100-01''), $d = 0.2$ (``mvcp100-02''), $d = 0.3$ (``mvcp100-03''), $d = 0.5$ (``mvcp100-04''), $d = 0.5$ (``mvcp100-05'') and the regular graph of size $n = 100 \ (k=32)$ from Papadimitriou and Steiglitz (``PS100'').%
 }
@@
 To test the behaviour of the genetic algorithm
-as well as the vercov algorithm for an even
+as well as the vercov heuristic for an even
 larger problem size, The same experiments
@@
 genetic algorithm are shown in table~\ref{tbl:t3}, while the results
-from the vercov algorithm are shown in table~\ref{tbl:t4}.
+from the vercov heuristic are shown in table~\ref{tbl:t4}.
 See the previous paragraphs for a better understanding of these results.
@@
 \includegraphics[width=1\textwidth]{t4}
-\caption[Results obtained by vercov algorithm for graphs in test set~2]{%
-Experimental results obtained by the vercov algorithm for five random graphs of size $n = 200$ with edge density: $d = 0.1$ (``mvcp200-01''), $d = 0.2$ (``mvcp200-02''), $d = 0.3$ (``mvcp200-03''), $d = 0.5$ (``mvcp200-04''), $d = 0.5$ (``mvcp200-05'') and the regular graph of size $n = 202 \ (k=66)$ from Papadimitriou and Steiglitz (``PS202'').%
+\caption[Results obtained by vercov heuristic for graphs in test set~2]{%
+Experimental results obtained by the vercov heuristic for five random graphs of size $n = 200$ with edge density: $d = 0.1$ (``mvcp200-01''), $d = 0.2$ (``mvcp200-02''), $d = 0.3$ (``mvcp200-03''), $d = 0.5$ (``mvcp200-04''), $d = 0.5$ (``mvcp200-05'') and the regular graph of size $n = 202 \ (k=66)$ from Papadimitriou and Steiglitz (``PS202'').%
 }
@@
 For the random graphs used to compare the
-genetic algorithm and the vercov algorithm,
+genetic algorithm and the vercov heuristic,
 it is known by construction that an optimum of
@@
 genetic algorithm almost surely finds the global optimum
-of the problems, while vercov algorithm gives
+of the problems, while vercov heuristic gives
 a relatively terrible results.
@@
 runs identify a solution of quality $2k + 2$.
-Whereas, vercov algorithm gives a solution of
+Whereas, vercov heuristic gives a solution of
 quality $2k + 2$ in all of the 100 runs as expected \cite{10:mvcp}.
 Recall that the graphs are constructed
-so as to force the vercov algorithm into yielding solutions
+so as to force the vercov heuristic into yielding solutions
 of quality $2k + 2$.
@@
 
-For the randomly constructed graphs, the vercov algorithm
+For the randomly constructed graphs, the vercov heuristic
 performs poorly.
@@
 and 172 (for graphs of size 200).
-The average performance of the vercov algorithm (surprisingly)
+Moreover, notice that the quality of its solutions are dominated
+by the quality of the solutions found by the genetic algorithm;
+the worst solutions found by the genetic algorithm are almost as
+good as the best solutions found by the vercov heuristic.
+
+The average performance of the vercov heuristic (surprisingly)
 decreases as the edge density is increased;
-i.e. the problems become even harder for the vercov algorithm
+i.e. the problems become even harder for the vercov heuristic
 while they become much simpler for the genetic algorithm when
@@
 The average fitness found by the genetic algorithm is notably
-better than the one found by the vercov algorithm.
+better than the one found by the vercov heuristic.
 One can demonstrate this by calculating
@@
 let $\bar{f}_1, \bar{f}_2$ be the average found by
-the genetic algorithm, vercov algorithm respectively.
+the genetic algorithm, vercov heuristic respectively.
 We have $ (\bar{f}_2 - 55) / (\bar{f}_1 - 55) = (86.46 - 55)/(62.61 - 55) \approx 4 = 400\%$
@@
 \section{Conclusion}
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
-tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
-quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
-consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
-cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
-proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-\cite[hi][go]{coley} \cite{davis}
+\label{sec:conc}
+This work has demonstrated that genetic algorithms can
+be used in a fairly straightforward way to find good
+approximative solutions for NP-hard problems, namely
+the minimum vertex cover problem.
+The robustness of the presented solution along with
+the positive results obtained support the idea
+that genetic algorithms are a desirable approach for tackling
+these type of problems.
+To tackle a new problem, rather than having to construct
+tailored heuristics to handle the problem under consideration,
+we advocate the use of genetic algorithms where the
+only change to perform is the formulation of a new fitness
+function.
 
@@
 
-\cleardoublepage\phantomsection\addcontentsline{toc}{section}{References}
+\phantomsection\addcontentsline{toc}{section}{References}
 %\bibliographystyle{abbrv}

### 2018-02-28 paper.tex
reduced margins
done

@@
 \usepackage{setspace}
+\usepackage{subcaption}
 \usepackage{hyperref}
-\usepackage[a4paper, total={6in, 8in}]{geometry}
+\usepackage[a4paper, total={6in, 8.5in}]{geometry}
 \usepackage{algorithm}
@@
 % table of contents page
-\setstretch{0.5}
 \phantomsection\addcontentsline{toc}{section}{Contents}
 \tableofcontents
-\setstretch{1.0}
 
@@
 
-\begin{figure}[!htbp]
+\begin{figure}[!htb]
 \centering
@@
 
-\begin{algorithm}[!htbp]
+\begin{algorithm}[!htb]
 \caption{GenticAlgorithm$\left( n, u, p_c, p_m, f \right)$}
@@
 Fortunately, a simpler and better algorithm exists.
-The following simple algorithm is surprisingly the
+The following simple algorithm~\ref{alg:vercov} is surprisingly the
 best approximation algorithm known for the mvcp \cite[p.~301]{9:mvcp}.
 
-\begin{algorithm}[!htbp]
+\begin{algorithm}[!htb]
 \caption{vercov($G = (V, E)$)}
@@
 
-\begin{algorithm}[!htbp]
+\begin{algorithm}[!htb]
 \caption{GenerateRandomGraph$(n, d, k)$}
@@
 
-\begin{table}[!htbp]
+\begin{table}[!htb]
 \centering
@@
 that is, the error was reduced by a factor of 4.
+This is further visualized in figure~\ref{fig:av} for the random graphs in
+test set~1 (figure on the left) and for the random graphs in test set~2 (figure on the right),
+where the average value found by each algorithm
+for each graph instance is plotted.
+
+\begin{figure}[!h]
+
+\begin{subfigure}{0.5\textwidth}
+\includegraphics[width=1\linewidth]{av1} 
+\end{subfigure}
+\begin{subfigure}{0.5\textwidth}
+\includegraphics[width=1\linewidth]{av2}
+\end{subfigure}
+
+\caption[average fitness value plotted against edge density]
+{%
+average fitness value found by GA and vercov heuristic plotted
+against the edge density for each random graph in test set~1 (the left figure) or~2
+(the right figure).%
+}
+\label{fig:av}
+\end{figure}
 
@@
 
-\pagebreak
+%\pagebreak
 

### 2018-02-28 paper.tex
fixed upper/lower cases typos

@@
 
-The outline of this paper is as follows: Firstly, Section~\ref{sec:ga} gives a
+The outline of this paper is as follows: Firstly, section~\ref{sec:ga} gives a
 short introduction to genetic algorithms, and explains briefly how they work.
@@
 and explains its representation for an application of the genetic algorithm.
-Lastly, Section~\ref{sec:exper} presents our experimental results and
+Lastly, section~\ref{sec:exper} presents our experimental results and
 points out the notable observations that can be drawn from these results.
@@
 
-\caption[average fitness value plotted against edge density]
+\caption[Average fitness value plotted against edge density]
 {%
-average fitness value found by GA and vercov heuristic plotted
-against the edge density for each random graph in test set~1 (the left figure) or~2
-(the right figure).%
+Average fitness value found by GA and vercov heuristic plotted
+against the edge density
+for each random graph in test set~1 (the left figure) and
+for each random graph in test set~2 (the right figure).%
 }

### 2018-03-19 paper.tex
added ga2.png
will be adding supervisors changes
added dr.desouki notes

@@
 General Supervisor:		&	\textit{Dr. Kadan Aljoumaa} \\
-Langauge Supervisor:	&	\textit{Mr. Fahmi Alammareen} \\
+Language Supervisor:	&	\textit{Mr. Fahmi Alammareen} \\
 \end{tabular}
@@
 it is trying to solve, and it is tightly coupled with observations made about the problem.
-The \textit{minimum vertex cover} problem is a typical example of such
+The \textit{minimum vertex cover problem (mvcp)} is a typical example of such
 problems \cite{wolfram:mvc}.
@@
 
-In this work, we present an alternative approach that
-uses \textit{genetic algorithms} as a generalized heuristic for
+This work presents an alternative approach that
+uses \textit{genetic algorithms (GAs)} as a generalized heuristic for
 solving NP-hard combinatorial optimization problems.
@@
 
-The outline of this paper is as follows: Firstly, section~\ref{sec:ga} gives a
+The outline of this paper is as follows: Section~\ref{sec:ga} gives a
 short introduction to genetic algorithms, and explains briefly how they work.
@@
 and explains its representation for an application of the genetic algorithm.
-Lastly, section~\ref{sec:exper} presents our experimental results and
+Lastly, section~\ref{sec:exper} presents the experimental results and
 points out the notable observations that can be drawn from these results.
@@
 \subsection{The Intuition Behind GAs}
-Genetic Algorithms (GAs) \cite{coley, goldberg} are population based
+Genetic Algorithms \cite{coley, goldberg} are population based
 search algorithms, where by repeated use of genetic operations,
 such as \textem{mutation}, \textem{selection}, \textem{crossover}, etc...
-Successive new generations of better populations in the direction of
+successive new generations of better populations in the direction of
 search objectives are created.
@@
 a method for mixing fragments of the better solutions to form new, on
-average even better solutions.
-Which permits the population to \textem{evolve} naturally.
+average, or even better solutions,
+which permits the population to \textem{evolve} naturally.
 
@@
 The recombination operator
-allows for the exchange of information between different individuals,
+allows the exchange of information between different individuals,
 and mutation introduces innovation into the population.
@@
 \centering
-\includegraphics[width=1\textwidth]{ga}
+\includegraphics[width=1\textwidth]{ga2}
 \caption{General schema for genetic algorithms}
@@
 linearly transformed before calculating selection probabilities.
-This technique known as linear dynamic scaling is commonly used
+This technique known as Linear Dynamic Scaling is commonly used
 in genetic algorithms \cite[pp.~123--124]{goldberg}.
@@
 \paragraph{Crossover}
-The recombination (crossover) operator allows for the
+The recombination (crossover) operator allows the
 exchange of information between different individuals.
@@
 by choosing a crossover point $ \chi \in \{1, \dots, n-1 \} $
-at random and exchanging all bits after the $ \chi^{\text{th}} $ one
+at random, and exchanging all bits after the $ \chi^{\text{th}} $ one
 between both individuals.
@@
 
-\State select $x, y$ from $P$ using proportional selection
+\State select $x, y$ from $P$ using proportional selection based on $f$
 \Comment{selection}
@@
 \]
-On particular, we have $e_{ii} = 0$.
+In particular, we have $e_{ii} = 0$.
 
@@
 An interesting property of the mvcp is that by
-solving it, we also have a solution for two other
+solving it, we also have a solution to two other
 graph problems: the \textit{maximum independent set problem}
@@
 
-Consequently, one can obtain a solution of the maximum independent set
+Consequently, one can obtain a solution to the maximum independent set
 problem by taking the complement of the solution to the minimum vertex cover
@@
 
-\subsection{Related Algorithms}
+\subsection{Minimum Vertex Cover Approximation Algorithms}
 \label{sec:ra}
@@
 
-They considered regular graphs\footnote{%
-by ``regular graphs'' we don't refer to the definition where
-each vertex has the same degree.
-}, each of which consists of three levels.
+They considered regular graphs, each of which consists of three levels.
 The first two levels have the same
@@
 nodes in addition to the nodes of the third level), while
-the optimal solution has size $k + 2$.
+the optimal solution has size $k + 2$~\cite{mvcp-back}.
 
 However this algorithm is not totally useless. It may be shown that it always
-achieves the ratio $\Theta(\lg n)$\footnote{$f(n) = \Theta(g(n)) \iff
+achieves the ratio $\Theta(\lg n)$\footnote[2]{$f(n) = \Theta(g(n)) \iff
 \exists \alpha, \beta, n_0 : \forall n \geq n_0, \ 
@@
 \subsection{Experimental Conclusions}
-From these tables, a number of interesting conclusions
-can be drawn.
-For the random graphs used to compare the
+Based on the results found in the previous section,
+one can observe a number of interesting facts.
+Recall that for the random graphs used to compare the
 genetic algorithm and the vercov heuristic,
@@
 for the test set~2).
-This optimum is likely to be the global optimum.
-And it is found by the genetic algorithm at least once
-within the $N = 100$ runs that were performed.
+This optimum is found by the genetic algorithm at least once
+within the $N = 100$ runs that were performed,
+and it is likely to be the global optimum.
 

### 2018-03-19 paper.tex
added amareen notes

@@
 would start with the nodes of the third level, since these
-have highest degree. Consequently, the greedy strategy
+have the highest degree. Consequently, the greedy strategy
 finds a solution of size $2k + 2$ (since it has to select $k + 2$
@@
 
-However this algorithm is not totally useless. It may be shown that it always
+However, this algorithm is not totally useless. It may be shown that it always
 achieves the ratio $\Theta(\lg n)$\footnote[2]{$f(n) = \Theta(g(n)) \iff
@@
 Consequently, any infeasible solution will have a fitness greater than
-or equal to $n$. And for any feasible solution the second term will
+or equal to $n$. And for any feasible solution, the second term will
 drop to zero, making the fitness value of the worst feasible solution at most $n$.
@@
 of the search space. In other words, the more edges a solution
-covers, the fitter it is. notice that this is guaranteed by the
+covers, the fitter it is. Notice that this is guaranteed by the
 second term in equation~\ref{eq:f}, where for each uncovered edge
@@
 as well as the vercov heuristic for an even
-larger problem size, The same experiments
+larger problem size, the same experiments
 were performed for larger graphs.
@@
 genetic algorithm almost surely finds the global optimum
-of the problems, while vercov heuristic gives
-a relatively terrible results.
+of the problems, while vercov heuristic gives relatively terrible results.
 
@@
 and 172 (for graphs of size 200).
-Moreover, notice that the quality of its solutions are dominated
+Moreover, notice that the quality of its solutions is dominated
 by the quality of the solutions found by the genetic algorithm;
@@
 that genetic algorithms are a desirable approach for tackling
-these type of problems.
+these types of problems.
 To tackle a new problem, rather than having to construct
